---
title: "index"
format: html
editor: visual
---

```{r}
library(apollo)

apollo_initialise()

```

# MNL - RUM For All Respondents

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean=mlogit_clean[c(1:11,15,19,38:47, 71)]
mlogit_clean$Alternative[which(mlogit_clean$Alternative==1)]="alt1"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="2")]="alt2"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_wide=reshape(mlogit_clean,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#viewpoint
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))

#Resident 
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL - Apollo code

b_HHIncome_num = 0,

```{r}

apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0, 
  b_resident            = 0,
  b_age                 = 0,
  b_education           = 0,
  #b_environment = 0, 
  #b_userfee = 0, 
  b_income              = 0, 
  b_sex = 0
)
apollo_fixed <- c()

```

```{r}

apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 +
    
    # person-specific covariates (shift alt1 vs opt-out)
    b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
    #b_environment* Member.Environment_binary +
    #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 +
    
    # person-specific covariates (shift alt2 vs opt-out)
    b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
    #b_environment* Member.Environment_binary +
   #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}

```

```{r}
model = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model)
```

```{r}

#Extract apollo model result 
est <- model$estimate

#Extract standard error
se <- sqrt(diag(model$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
coef_table <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# RUM For Trails (Residents Only)

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean_Residents=mlogit_clean_Residents[c(1:11,15,19,38:47, 71)]
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative==1)]="alt1"
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative=="2")]="alt2"
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_Residents_wide=reshape(mlogit_clean_Residents,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_Residents_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL Resident - Apollo code

b_HHIncome_num = 0,

```{r}
apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0, 
  b_age                 = 0,
  b_education           = 0,
  #b_environment = 0, 
  b_income              = 0, 
  b_sex = 0
)
apollo_fixed <- c()


apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 +
    
    # person-specific covariates (shift alt1 vs opt-out)
    #b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
   #b_environment* Member.Environment_binary +
    #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 +
    
    # person-specific covariates (shift alt2 vs opt-out)
   # b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
    #b_environment* Member.Environment_binary +
   #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}
```

```{r}
model_residents = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model_residents)
```

```{r}

# Extract Apollo model results
est.residents <- model_residents$estimate

# Extract standard errors
se.residents <- sqrt(diag(model_residents$robvarcov))

# Create coefficient table
coef_residents <- tibble(
  Parameter = names(est.residents),
  Estimate  = est.residents,
  SE        = se.residents[names(est.residents)]
)

# Add significance stars
coef_residents <- coef_residents %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# RUM For Trails (Tourists Only)

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis

mlogit_clean_Tourists=mlogit_clean_Tourists[c(1:11,15,19,38:47, 71)]
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative==1)]="alt1"
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative=="2")]="alt2"
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_Tourists_wide=reshape(mlogit_clean_Tourists,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_Tourists_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL Tourist Apollo code

b_HHIncome_num = 0,

```{r}

apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow        = 0,
  b_cost                = 0,
  asc_optout            = 0, 
  b_age                 = 0,
  b_education           = 0,
  #b_environment = 0, 
  b_income              = 0, 
  b_sex = 0
)
apollo_fixed <- c()


apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 +
    
    # person-specific covariates (shift alt1 vs opt-out)
    #b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
   #b_environment* Member.Environment_binary +
    #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 +
    
    # person-specific covariates (shift alt2 vs opt-out)
   # b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
    #b_environment* Member.Environment_binary +
   #b_userfee    * WTP_User.fee_binary +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}
```

```{r}
model_tourists = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model_tourists)
```

```{r}

# Extract Apollo model results
est.tourists <- model_tourists$estimate

# Extract standard errors
se.tourists<- sqrt(diag(model_tourists$robvarcov))

# Create coefficient table
coef_tourists <- tibble(
  Parameter = names(est.tourists),
  Estimate  = est.tourists,
  SE        = se.residents[names(est.tourists)]
)

# Add significance stars
coef_tourists <- coef_tourists%>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# MXL For All Respondents

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_wide
```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Crowding viewpoint
database %<>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))


#Resident 
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
# #Crowding with water fall 
#   b_CrowdingM_WF        = 0,
#   b_CrowdingL_WF        = 0,
  b_cost                = 0,
  asc_optout            = 0, 

  # sociodems (fixed)
    b_resident  = 0,
    b_age       = 0,
    b_education = 0,
    b_income    = 0,
    b_sex       = 0,

  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1 
)
apollo_fixed <- c()

```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow
  

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
 # b_CrowdingM_WF           * CrowdingM_WF.alt1 + 
 # b_CrowdingL_WF          * CrowdingL_WF.alt1 +
  b_cost                  * Cost.alt1 +
  b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
 # b_CrowdingM_WF           * CrowdingM_WF.alt2 + 
 # b_CrowdingL_WF          * CrowdingL_WF.alt2 +
   b_cost                  * Cost.alt2 +
   b_resident   * Resident +
   b_age        * Demo_Age_num +
   b_education  * CollegePlus +
   b_income     * HHIncome_num +
   b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
 # V[["alt3"]] = 0
    # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
model_mxl <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl)
```

```{r}

#Extract apollo model result 
est <- model_mxl$estimate

#Extract standard error
se <- sqrt(diag(model_mxl$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# MXL For Trails (Residents Only)

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_Residents_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout  = 0,   

  # sociodems (fixed)
   #b_resident  = 0,
   b_age       = 0,
   b_education = 0,
   b_income    = 0,
   b_sex       = 0,

  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)
apollo_fixed <- c()

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  b_cost                  * Cost.alt1 +
 #b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  b_cost                  * Cost.alt2 +
   #b_resident   * Resident +
   b_age        * Demo_Age_num +
   b_education  * CollegePlus +
   b_income     * HHIncome_num +
   b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
 # V[["alt3"]] = 0
    # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}
```

```{r}
model_mxl_Resident <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl_Resident)
```

```{r}

#Extract apollo model result 
est <- model_mxl_Resident$estimate

#Extract standard error
se <- sqrt(diag(model_mxl_Resident$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table_Resident <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# MXL For Trails (Tourist Only)

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_Tourists_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout = 0,

  # sociodems (fixed)
  #b_resident  = 0,
    b_age       = 0,
    b_education = 0,
    b_income    = 0,
    b_sex       = 0,


  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)
apollo_fixed <- c()

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  b_cost                  * Cost.alt1 +
  # # #b_resident   * Resident +
    b_age        * Demo_Age_num +
   b_education  * CollegePlus +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  b_cost                  * Cost.alt2 +
  # #b_resident   * Resident +
    b_age        * Demo_Age_num +
    b_education  * CollegePlus +
    b_income     * HHIncome_num +
    b_sex        * Sex_binary
   
  # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
model_mxl_Tourist <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl_Tourist)
```

```{r}

#Extract apollo model result 
est <- model_mxl_Tourist$estimate

#Extract standard error
se <- sqrt(diag(model_mxl_Tourist$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table_Tourist <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# **Create Utility Table: Combine output: Stargazer**

```{r}
get_apollo_stargazer_inputs <- function(model, robust = TRUE, p_sided = 2) {
  M <- as.matrix(apollo_modelOutput(model, modelOutput_settings = list(silent = TRUE)))

  b <- M[, "Estimate"]

  if (robust) {
    se <- M[, "Rob.s.e."]
    t  <- M[, "Rob.t.rat.(0)"]
  } else {
    se <- M[, "s.e."]
    t  <- M[, "t.rat.(0)"]
  }

  # p-values from t-ratio (normal approximation)
  if (p_sided == 1) {
    p <- 1 - pnorm(abs(t))             # 1-sided
  } else {
    p <- 2 * (1 - pnorm(abs(t)))       # 2-sided
  }

  names(b)  <- rownames(M)
  names(se) <- rownames(M)
  names(p)  <- rownames(M)

  list(b = b, se = se, p = p)
}

align_to <- function(x, order) {
  out <- rep(NA_real_, length(order))
  names(out) <- order
  out[names(x)] <- x
  out
}

make_dummy_lm_named <- function(coef_names, n = 100, seed = 1) {
  set.seed(seed)
  K <- length(coef_names)
  X <- as.data.frame(matrix(rnorm(n * K), nrow = n, ncol = K))
  names(X) <- coef_names
  X$y <- rnorm(n)
  lm(y ~ 0 + ., data = X)  # no intercept
}
```

```{r}
#library(stargazer)

# Extract
v_MNL_all  <- get_apollo_stargazer_inputs(model,      robust = TRUE, p_sided = 2)
v_MNL_res  <- get_apollo_stargazer_inputs(model_residents, robust = TRUE, p_sided = 2)
v_MNL_tour <- get_apollo_stargazer_inputs(model_tourists,  robust = TRUE, p_sided = 2)
v_MXL_all  <- get_apollo_stargazer_inputs(model_mxl,      robust = TRUE, p_sided = 2)
v_MXL_res  <- get_apollo_stargazer_inputs(model_mxl_Resident, robust = TRUE, p_sided = 2)
v_MXL_tour <- get_apollo_stargazer_inputs(model_mxl_Tourist,  robust = TRUE, p_sided = 2)

# Choose your row order (edit if needed)
order <- c(
  "b_Habitat_QualityMed","b_Habitat_QualityHigh",
  "b_Trail_ConditionMed","b_Trail_ConditionHigh",
  "b_CrowdingMed","b_CrowdingLow", "asc_optout",
  "b_cost",
  "b_resident",
  "b_age","b_education","b_income","b_sex",


  "sd_Habitat_QualityMed","sd_Habitat_QualityHigh",
  "sd_Trail_ConditionMed","sd_Trail_ConditionHigh",
  "sd_CrowdingMed","sd_CrowdingLow"
)


labels <- c(
  "Habitat quality (Medium)","Habitat quality (High)",
  "Trail condition (Medium)","Trail condition (High)",
  "Crowding (Medium)","Crowding (Low)","ASC",
  "Cost",
  "Resident",
  "Age","Education","Income","Sex",
  "SD: Habitat quality (Medium)","SD: Habitat quality (High)",
  "SD: Trail condition (Medium)","SD: Trail condition (High)",
  "SD: Crowding (Medium)","SD: Crowding (Low)"
)


# Align each model’s vectors to the same coefficient list
coef_list <- list(
  align_to(v_MNL_all$b,  order),
  align_to(v_MNL_res$b,  order),
  align_to(v_MNL_tour$b, order),
  align_to(v_MXL_all$b,  order),
  align_to(v_MXL_res$b,  order),
  align_to(v_MXL_tour$b, order)
)

se_list <- list(
  align_to(v_MNL_all$se,  order),
  align_to(v_MNL_res$se,  order),
  align_to(v_MNL_tour$se, order),
  align_to(v_MXL_all$se,  order),
  align_to(v_MXL_res$se,  order),
  align_to(v_MXL_tour$se, order)
)

p_list <- list(
  align_to(v_MNL_all$p,  order),
  align_to(v_MNL_res$p,  order),
  align_to(v_MNL_tour$p, order),
  align_to(v_MXL_all$p,  order),
  align_to(v_MXL_res$p,  order),
  align_to(v_MXL_tour$p, order)
)

# Dummy models for stargazer
make_dummy_lm_named <- function(coef_names, n = 100, seed = 1) {
  set.seed(seed)
  K <- length(coef_names)
  X <- as.data.frame(matrix(rnorm(n * K), nrow = n, ncol = K))
  names(X) <- coef_names
  X$y <- rnorm(n)
  lm(y ~ 0 + ., data = X)  # no intercept, so exactly K coefs with these names
}

d1 <- make_dummy_lm_named(order, seed = 1)
d2 <- make_dummy_lm_named(order, seed = 2)
d3 <- make_dummy_lm_named(order, seed = 3)
d4 <- make_dummy_lm_named(order, seed = 4)
d5 <- make_dummy_lm_named(order, seed = 5)
d6 <- make_dummy_lm_named(order, seed = 6)



```

```{r}
obs <- c(model$nObs, model_residents$nObs, model_tourists$nObs,
         model_mxl$nObs, model_mxl_Resident$nObs, model_mxl_Tourist$nObs)

resp <- c(model$nIndivs, model_residents$nIndivs, model_tourists$nIndivs,
          model_mxl$nIndivs, model_mxl_Resident$nIndivs, model_mxl_Tourist$nIndivs)

aic <- round(c(model$AIC, model_residents$AIC, model_tourists$AIC,
               model_mxl$AIC, model_mxl_Resident$AIC, model_mxl_Tourist$AIC), 2)


```

```{r}
#Combined MXL and MNL 

stargazer(
 d1, d2, d3, d4, d5, d6, 
  type = "html",
  out  = "Mnl_Mxl_table.html",
  title = "Trail Choice Model Results",

  column.labels   = c("MNL", "MXL"),
  column.separate = c(3, 3),

  model.numbers = TRUE,            # shows (1)-(6)
  dep.var.labels.include = FALSE,

  covariate.labels = labels,
  coef = coef_list, se = se_list, p = p_list,
  omit.stat = c("n","f","ser","adj.rsq","rsq"),
  add.lines = list(
    c("Observations", obs),
    c("Respondents",  resp),
    c("AIC",          aic)
  ),
  notes = "Columns (1)-(3): All / Residents / Tourists (MNL). Columns (4)-(6): All / Residents / Tourists (MXL). SE in parentheses.",
  notes.append = FALSE
)




```

```{r}
#Only MNL model 
stargazer(
  d1, d2, d3,
  type = "html",
  out  = "MNL_table1.html",
  title = "Multinomial Logit Model Results",

  model.numbers = FALSE,
  dep.var.labels.include = FALSE,

  column.labels = c("All respondents", "Residents", "Tourists"),
  column.separate = c(1,1,1),

  covariate.labels = labels,

  coef = coef_list[1:3],
  se   = se_list[1:3],
  p    = p_list[1:3],

  omit.stat = c("n","f","ser","adj.rsq","rsq"),

  add.lines = list(
    c("Observations", obs[1:3]),
    c("Respondents",  resp[1:3]),
    c("AIC",          aic[1:3])
  ),

  notes = "Robust standard errors in parentheses.",
  notes.append = FALSE
)

#Only MXL model 
stargazer(
  d4, d5, d6,
  type = "html",
  out  = "MXL_table1.html",
  title = "Mixed Logit (MXL) Model Results",

  model.numbers = FALSE,
  dep.var.labels.include = FALSE,

  column.labels = c("All respondents", "Residents", "Tourists"),
  column.separate = c(1,1,1),

  covariate.labels = labels,

  coef = coef_list[4:6],
  se   = se_list[4:6],
  p    = p_list[4:6],

  omit.stat = c("n","f","ser","adj.rsq","rsq"),

  add.lines = list(
    c("Observations", obs[4:6]),
    c("Respondents",  resp[4:6]),
    c("AIC",          aic[4:6])
  ),

  notes = "Robust standard errors in parentheses.",
  notes.append = FALSE
)
```

# WTP Mean

```{r}

# Attributes you want WTP for (these are the *mean* taste parameters)
wtp_pars <- c(
  "b_Habitat_QualityMed",
  "b_Habitat_QualityHigh",
  "b_Trail_ConditionMed",
  "b_Trail_ConditionHigh",
  "b_CrowdingMed",
  "b_CrowdingLow"
)

cost_par <- "b_cost"   # <- fixed cost coefficient name in the fixed-cost model

```

```{r}
wtp_delta <- function(model, wtp_pars, cost_par = "b_cost", use_robust = TRUE){
  bhat <- model$estimate
  Vhat <- if(use_robust) (model$robvarcov %||% model$varcov) else model$varcov
  if(is.null(Vhat)) stop("No varcov/robvarcov found in model object.")

  needed <- c(wtp_pars, cost_par)
  missing <- setdiff(needed, names(bhat))
  if(length(missing) > 0) stop("Missing parameters in model$estimate: ", paste(missing, collapse=", "))

  bc <- as.numeric(bhat[cost_par])
  if(is.na(bc)) stop("Cost parameter not found.")

  out <- lapply(wtp_pars, function(p){
    bk <- as.numeric(bhat[p])

    wtp <- -bk / bc

    # gradient vector aligned to (bk, bc)
    g <- c(d_bk = -1/bc,
           d_bc =  bk/(bc^2))

    # extract 2x2 varcov for (bk, bc)
    V2 <- as.matrix(Vhat[c(p, cost_par), c(p, cost_par)])

    var_wtp <- as.numeric(t(g) %*% V2 %*% g)
    se_wtp  <- sqrt(var_wtp)

    tibble(
      Attribute = p,
      wtp = wtp,
      lo95 = wtp - 1.96 * se_wtp,
      hi95 = wtp + 1.96 * se_wtp
    )
  })

  bind_rows(out)
}

```

```{r}
# wtp_krinsky_robb <- function(model, wtp_pars, cost_par="b_cost",
#                              R = 20000, use_robust = TRUE, seed = 123){
#   set.seed(seed)
# 
#   bhat <- model$estimate
#   Vhat <- if(use_robust) (model$robvarcov %||% model$varcov) else model$varcov
#   if(is.null(Vhat)) stop("No varcov/robvarcov found in model object.")
# 
#   needed <- c(wtp_pars, cost_par)
#   missing <- setdiff(needed, names(bhat))
#   if(length(missing) > 0) stop("Missing parameters in model$estimate: ", paste(missing, collapse=", "))
# 
#   # Work on the subset vector (wtp_pars + cost_par)
#   pars <- c(wtp_pars, cost_par)
#   mu   <- as.numeric(bhat[pars])
#   Sig  <- as.matrix(Vhat[pars, pars])
# 
#   draws <- MASS::mvrnorm(n = R, mu = mu, Sigma = Sig)
#   colnames(draws) <- pars
# 
#   bc_draw <- draws[, cost_par]
# 
#   # WTP draws for each attribute
#   wtp_draws <- sapply(wtp_pars, function(p){
#     -draws[, p] / bc_draw
#   })
#   colnames(wtp_draws) <- wtp_pars
# 
#   # Point estimate from bhat (same formula)
#   bc <- as.numeric(bhat[cost_par])
# 
#   tibble(
#     Attribute = wtp_pars,
#     wtp  = -as.numeric(bhat[wtp_pars]) / bc,
#     lo95 = apply(wtp_draws, 2, quantile, 0.025, na.rm=TRUE),
#     hi95 = apply(wtp_draws, 2, quantile, 0.975, na.rm=TRUE)
#   )
# }

```

```{r}
# wtp_all  <- wtp_krinsky_robb(model_mxl,  wtp_pars, cost_par, R=20000, seed=1)
# wtp_res  <- wtp_krinsky_robb(model_mxl_Resident,  wtp_pars, cost_par, R=20000, seed=2)
# wtp_tour <- wtp_krinsky_robb(model_mxl_Tourist, wtp_pars, cost_par, R=20000, seed=3)


```

```{r}
 wtp_all_delta  <- wtp_delta(model_mxl, wtp_pars, cost_par)
 wtp_res_delta  <- wtp_delta(model_mxl_Resident,  wtp_pars, cost_par)
 wtp_tour_delta<- wtp_delta(model_mxl_Tourist, wtp_pars, cost_par)

```

```{r}
# fmt_cell <- function(est, lo, hi, digits=2){
#   sprintf(paste0("%.",digits,"f (%.",digits,"f\u2013%.",digits,"f)"), est, lo, hi)
# }
# 
# order_pars <- wtp_pars
# row_labels <- c(
#   "Habitat Quality: Medium",
#   "Habitat Quality: High",
#   "Trail Condition: Medium",
#   "Trail Condition: High",
#   "Crowding: Medium",
#   "Crowding: Low"
# )
# 
# prep_col <- function(df){
#   df <- df[match(order_pars, df$Attribute), ]
#   mapply(fmt_cell, df$wtp, df$lo95, df$hi95, MoreArgs=list(digits=2))
# }
# 
# wtp_table <- data.frame(
#   `Attributes` = row_labels,
#   `All respondents` = prep_col(wtp_all_delta),
#   `Residents`       = prep_col(wtp_res_delta),
#   `Tourists`        = prep_col(wtp_tour_delta),
#   check.names = FALSE
# )

# stargazer(wtp_table,
#           summary = FALSE,
#           rownames = FALSE,
#           title = "Willingness to pay per entrance for trail improvements across groups.",
#           notes = "95% confidence intervals in parentheses",
#           type = "text")

```

```{r}
# stargazer(
#   wtp_table,
#   summary = FALSE,
#   rownames = FALSE,
#   title = "Willingness to pay per trip for trail improvements across groups.",
#   notes = "95% confidence intervals in parentheses.",
#   type = "html",
#   out  = "WTP_table.html"
# )

```

```{r}
# First, let's get the data in the right format
order_pars <- wtp_pars
row_labels <- c(
  "Habitat Quality: Medium",
  "Habitat Quality: High",
  "Trail Condition: Medium", 
  "Trail Condition: High",
  "Crowding: Medium",
  "Crowding: Low"
)

# Create a function to prepare data for stargazer with two rows per attribute
create_stargazer_data <- function(wtp_all, wtp_res, wtp_tour) {
  # Reorder to match the desired order
  wtp_all <- wtp_all[match(order_pars, wtp_all$Attribute), ]
  wtp_res <- wtp_res[match(order_pars, wtp_res$Attribute), ]
  wtp_tour <- wtp_tour[match(order_pars, wtp_tour$Attribute), ]
  
  # Initialize vectors for the table
  attributes_col <- character()
  all_resp_col <- character()
  residents_col <- character()
  tourists_col <- character()
  
  # For each attribute, add two rows: one for mean, one for CI
for(i in 1:nrow(wtp_all)) {
    # Row 1: Mean value
attributes_col <- c(attributes_col, row_labels[i])
all_resp_col   <- c(all_resp_col,  sprintf("DOLLARSIGN%.0f", wtp_all$wtp[i]))
residents_col  <- c(residents_col, sprintf("DOLLARSIGN%.0f", wtp_res$wtp[i]))
tourists_col   <- c(tourists_col,  sprintf("DOLLARSIGN%.0f", wtp_tour$wtp[i]))


    # Row 2: Confidence interval
    attributes_col <- c(attributes_col, "")
    all_resp_col <- c(all_resp_col, sprintf("(%.0f\u2013%.0f)", wtp_all$lo95[i], wtp_all$hi95[i]))
    residents_col <- c(residents_col, sprintf("(%.0f\u2013%.0f)", wtp_res$lo95[i], wtp_res$hi95[i]))
    tourists_col <- c(tourists_col, sprintf("(%.0f\u2013%.0f)", wtp_tour$lo95[i], wtp_tour$hi95[i]))
  }
  
  # Create the data frame
  data.frame(
    Attributes = attributes_col,
    `All respondents` = all_resp_col,
    Residents = residents_col,
    Tourists = tourists_col,
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
}

# Create the table data
stargazer_data <- create_stargazer_data(wtp_all_delta, wtp_res_delta, wtp_tour_delta)

# Create the table with stargazer
stargazer(
  stargazer_data,
  summary = FALSE,
  rownames = FALSE,
  title = "Willingness to pay per use for trail improvements across groups.",
  notes = "95% confidence intervals in parentheses.",
  type = "html",
  out = "WTP_table.CI.html",
  # Add styling to improve appearance
  column.sep.width = "10pt",
  font.size = "small",
  # Remove default note about number of observations
  notes.align = "l",
  notes.append = FALSE
)

# Then replace the placeholder with $ in the output file
html_content <- readLines("WTP_table.CI.html")
html_content <- gsub("DOLLARSIGN", "$", html_content, fixed = TRUE)
writeLines(html_content, "WTP_table.CI.html")
```

# WTP Graph: TC and HQ

```{r}
# --- Step 1: Create Attribute level table 
attr_levels <- data.frame(
  Attribute = c("b_Habitat_QualityMed", "b_Habitat_QualityHigh", "b_Trail_ConditionMed", "b_Trail_ConditionHigh"),
  AttributeName = c("Habitat Quality", "Habitat Quality", "Trail Condition", "Trail Condition"),
  Level = c("Medium", "High", "Medium", "High"),
  stringsAsFactors = FALSE
)

wtp_all  <- wtp_all_delta  %>% mutate(Group = "All respondents")
wtp_res  <- wtp_res_delta  %>% mutate(Group = "Residents")
wtp_tour <- wtp_tour_delta %>% mutate(Group = "Tourists")

wtp_combined <- bind_rows(wtp_all, wtp_res, wtp_tour) %>%
  right_join(attr_levels, by = "Attribute")

# --- Step 2: Build gap annotation data (Tourists minus Residents, at "High" level)
gap_data <- wtp_combined %>%
  filter(Group %in% c("Residents", "Tourists")) %>%
  select(AttributeName, Level, Group, wtp) %>%
  pivot_wider(names_from = Group, values_from = wtp) %>%33
  mutate(
    gap = round(Tourists - Residents),        # rounded difference
    label = paste0("+$", gap)                 # label e.g. "+$52"
  )

group_colors <- c("All respondents" = "grey", "Residents" = "#6a906c", "Tourists" = "#ae9864")

p <- ggplot(wtp_combined, aes(x = Level, y = wtp, color = Group, group = Group)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  # Rounded value labels above points
  geom_text(aes(label = paste0("$", round(wtp))),
            vjust = -0.8,
            size = 3,
            show.legend = FALSE,
            fontface = "bold",
            color = "black") +
  # # Gap bracket: vertical segment between Residents and Tourists
  # geom_segment(
  #   data = gap_data,
  #   aes(x = Level, xend = Level,
  #       y = Residents, yend = Tourists),
  #   inherit.aes = FALSE,
  #   color = "black",
  #   linewidth = 0.6,
  #   linetype = "dashed",
  #   arrow = arrow(ends = "both", length = unit(0.15, "cm"), type = "closed")
  # ) +
  # # Gap label to the right of the bracket
  # geom_text(
  #   data = gap_data,
  #   aes(x = Level,
  #       y = (Residents + Tourists) / 2,
  #       label = label),
  #   inherit.aes = FALSE,
  #   hjust = -0.2,
  #   size = 3,
  #   color = "black"
  # ) +
  facet_wrap(~ AttributeName, scales = "free_y") +
  scale_color_manual(values = group_colors) +
  scale_y_continuous(limits = c(0, 110)) +
  labs(
    title = "Willingness to Pay for Trail Improvements",
    x = "Management Level",
    y = "Average WTP per use ($)",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +
 theme(
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 16),   # facet titles: "Habitat Quality", "Trail Condition"
    legend.text  = element_text(size = 13),                # group names in legend
    legend.title = element_blank(),, # "Group" label
      panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(size = 12)

  )

print(p)
ggsave("WTP_incremental.png", p, width = 10, height = 6, dpi = 300)
```

# WTP Graph: Crowding

```{r}
# --- Step 1: Create Attribute level table 
attr_levels_crowding <- data.frame(
  Attribute = c("b_CrowdingMed", "b_CrowdingLow"),
  AttributeName = c("Crowding", "Crowding"),
  Level = c("Medium", "Low"),
  stringsAsFactors = FALSE
)

# Combine groups
wtp_all <- wtp_all_delta %>% mutate(Group = "All respondents")
wtp_res <- wtp_res_delta %>% mutate(Group = "Residents")
wtp_tour <- wtp_tour_delta %>% mutate(Group = "Tourists")

wtp_combined_crowding <- bind_rows(wtp_all, wtp_res, wtp_tour) %>%
  right_join(attr_levels_crowding, by = "Attribute")
```

```{r}
group_colors <- c("All respondents" = "grey", "Residents" = "#6a906c", "Tourists" = "#ae9864")

r <- ggplot(wtp_combined_crowding, aes(x = Level, y = wtp, color = Group, group = Group)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  # geom_errorbar(aes(ymin = lo95, ymax = hi95), width = 0.1, size = 0.5) +
  # Add value labels above points
  geom_text(aes(label = paste0("$", round(wtp))),
            vjust = -0.8,
            size = 3,
            show.legend = FALSE,
            fontface = "bold",
            color = "black") +     # use black for readability (or match group colors)
  facet_wrap(~ AttributeName, scales = "free_y") +
  scale_color_manual(values = group_colors) +
   scale_y_continuous(limits = c(0, 100)) + 
  labs(
    title = "Willingness to Pay for Trail Improvements",
    x = "Management Level",
    y = "Average WTP per use ($)",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +
 theme(
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 16),   # facet titles: "Crowding"
    legend.text  = element_text(size = 13),                # group names in legend
    legend.title = element_blank(),, # "Group" label
      panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(size = 12)

  )


print(r)
ggsave("WTP_incremental_Crowding.png", r, width = 10, height = 6, dpi = 300)
```

# Welfare Calculation

```{r}
# ══════════════════════════════════════════════════════
# WELFARE / COMPENSATING VARIATION CALCULATION
# Policy Scenarios: Baseline → Medium → High Improvement
# Method: Small-Rosen logsum formula
# ══════════════════════════════════════════════════════

library(tibble)
library(dplyr)

# ── Step 1: Extract coefficients from pooled MXL model ──
bhat <- model_mxl$estimate

b_HabitatMed   <- bhat["b_Habitat_QualityMed"]
b_HabitatHigh  <- bhat["b_Habitat_QualityHigh"]
b_TrailCondMed <- bhat["b_Trail_ConditionMed"]
b_TrailCondHigh<- bhat["b_Trail_ConditionHigh"]
b_CrowdingMed  <- bhat["b_CrowdingMed"]
b_CrowdingLow  <- bhat["b_CrowdingLow"]
b_cost         <- bhat["b_cost"]
asc_optout     <- bhat["asc_optout"]

cat("Extracted coefficients:\n")
cat("b_HabitatMed:   ", round(b_HabitatMed,   4), "\n")
cat("b_HabitatHigh:  ", round(b_HabitatHigh,  4), "\n")
cat("b_TrailCondMed: ", round(b_TrailCondMed, 4), "\n")
cat("b_TrailCondHigh:", round(b_TrailCondHigh,4), "\n")
cat("b_CrowdingMed:  ", round(b_CrowdingMed,  4), "\n")
cat("b_CrowdingLow:  ", round(b_CrowdingLow,  4), "\n")
cat("b_cost:         ", round(b_cost,          4), "\n")
cat("asc_optout:     ", round(asc_optout,      4), "\n")

```

```{r}

# ══════════════════════════════════════════════════════
# Step 2: Define scenario deterministic utilities
# ══════════════════════════════════════════════════════
# Notes:
# - Alt1 and Alt2 are trail alternatives (vary by cost)
# - Alt3 is opt-out (ASC only, no attributes)
# - Baseline: all attributes at reference level (dummies = 0)
# - We use mean cost across all alternatives as representative cost
# - Attribute utility is added on top of cost utility

# ── Mean cost across alt1 and alt2 in dataset ──
mean_cost <- mean(c(database$Cost.alt1, database$Cost.alt2), na.rm = TRUE)
cat("\nMean cost used in welfare calculation: $", round(mean_cost, 2), "\n")

# ── Scenario attribute utility components ──
# (cost term is the same across scenarios — cancels in CS difference)

# Baseline: Low habitat, Low trail condition, High crowding
# All attribute dummies = 0 → no attribute utility
V_attr_baseline <- 0

# Medium improvement: Medium habitat, Medium trail condition, Medium crowding
V_attr_medium <- b_HabitatMed + b_TrailCondMed + b_CrowdingMed

# High improvement: High habitat, High trail condition, Low crowding
V_attr_high <- b_HabitatHigh + b_TrailCondHigh + b_CrowdingLow

cat("\nAttribute utility components:\n")
cat("Baseline:          ", round(V_attr_baseline, 4), "\n")
cat("Medium improvement:", round(V_attr_medium,   4), "\n")
cat("High improvement:  ", round(V_attr_high,     4), "\n")

```

```{r}

# ══════════════════════════════════════════════════════
# Step 3: Compute logsum per scenario
# ══════════════════════════════════════════════════════
# Logsum = log[exp(V_alt1) + exp(V_alt2) + exp(V_alt3)]
# V_alt1 = V_attr + b_cost * cost_alt1  (per observation)
# V_alt2 = V_attr + b_cost * cost_alt2  (per observation)
# V_alt3 = asc_optout

compute_logsum <- function(V_attr, cost_alt1, cost_alt2, b_cost, asc_optout) {
  V1 <- V_attr + b_cost * cost_alt1
  V2 <- V_attr + b_cost * cost_alt2
  V3 <- rep(asc_optout, length(cost_alt1))
  
  # Small-Rosen logsum per choice occasion
  logsum <- log(exp(V1) + exp(V2) + exp(V3))
  return(logsum)
}

# ── Compute logsum for each scenario across all choice occasions ──
ls_baseline <- compute_logsum(
  V_attr_baseline, 
  database$Cost.alt1, database$Cost.alt2,
  b_cost, asc_optout)

ls_medium <- compute_logsum(
  V_attr_medium,
  database$Cost.alt1, database$Cost.alt2,
  b_cost, asc_optout)

ls_high <- compute_logsum(
  V_attr_high,
  database$Cost.alt1, database$Cost.alt2,
  b_cost, asc_optout)

cat("\nMean logsum per scenario:\n")
cat("Baseline: ", round(mean(ls_baseline), 4), "\n")
cat("Medium:   ", round(mean(ls_medium),   4), "\n")
cat("High:     ", round(mean(ls_high),     4), "\n")

```

```{r}
# ══════════════════════════════════════════════════════
# Step 4: Aggregate logsum to respondent level
# (panel structure — average across choice tasks per person)
# ══════════════════════════════════════════════════════
database$ls_baseline <- ls_baseline
database$ls_medium   <- ls_medium
database$ls_high     <- ls_high

respondent_logsum <- database %>%
  group_by(RID) %>%
  summarise(
    ls_baseline = mean(ls_baseline),
    ls_medium   = mean(ls_medium),
    ls_high     = mean(ls_high),
    .groups     = "drop"
  )

cat("\nRespondent-level mean logsums:\n")
cat("Baseline: ", round(mean(respondent_logsum$ls_baseline), 4), "\n")
cat("Medium:   ", round(mean(respondent_logsum$ls_medium),   4), "\n")
cat("High:     ", round(mean(respondent_logsum$ls_high),     4), "\n")

```

```{r}
# ══════════════════════════════════════════════════════
# Step 5: Compute Compensating Variation (CV)
# CV = [logsum(scenario) - logsum(baseline)] / (-b_cost)
# ══════════════════════════════════════════════════════
respondent_logsum$CV_medium <- (respondent_logsum$ls_medium - 
                                 respondent_logsum$ls_baseline) / (-b_cost)

respondent_logsum$CV_high   <- (respondent_logsum$ls_high - 
                                 respondent_logsum$ls_baseline) / (-b_cost)

cat("\n═══════════════════════════════════════════════\n")
cat("Compensating Variation — Per Trip, Per Person\n")
cat("═══════════════════════════════════════════════\n")
cat("CV Medium improvement: $", round(mean(respondent_logsum$CV_medium), 2), "\n")
cat("CV High improvement:   $", round(mean(respondent_logsum$CV_high),   2), "\n")
cat("═══════════════════════════════════════════════\n")


```

```{r}
# ══════════════════════════════════════════════════════
# Step 6: Delta method standard errors for CV
# ══════════════════════════════════════════════════════
Vhat <- model_mxl$robvarcov

cv_delta_se <- function(attr_pars, cost_par, model, scenario_name) {
  bhat <- model$estimate
  Vhat <- model$robvarcov
  bc   <- bhat[cost_par]
  
  # Sum of attribute coefficients for this scenario
  b_attr_sum <- sum(bhat[attr_pars])
  
  # CV point estimate (at mean cost — cost cancels in logsum difference)
  # CV = b_attr_sum / (-bc)  [simplified for linear utility]
  cv <- b_attr_sum / (-bc)
  
  # Gradient with respect to each attribute parameter and cost
  n_attr <- length(attr_pars)
  grad <- c(rep(1/(-bc), n_attr),        # d(CV)/d(b_attr_k) = 1/(-bc)
            b_attr_sum / (bc^2))          # d(CV)/d(bc)
  
  # Extract relevant varcov block
  all_pars <- c(attr_pars, cost_par)
  V2 <- as.matrix(Vhat[all_pars, all_pars])
  
  var_cv <- as.numeric(t(grad) %*% V2 %*% grad)
  se_cv  <- sqrt(var_cv)
  
  tibble(
    Scenario = scenario_name,
    CV       = round(cv, 2),
    SE       = round(se_cv, 2),
    CI_low   = round(cv - 1.96 * se_cv, 2),
    CI_high  = round(cv + 1.96 * se_cv, 2)
  )
}

# ── Medium scenario: HabitatMed + TrailCondMed + CrowdingMed ──
cv_medium_se <- cv_delta_se(
  attr_pars     = c("b_Habitat_QualityMed", 
                    "b_Trail_ConditionMed", 
                    "b_CrowdingMed"),
  cost_par      = "b_cost",
  model         = model_mxl,
  scenario_name = "Medium Improvement"
)

# ── High scenario: HabitatHigh + TrailCondHigh + CrowdingLow ──
cv_high_se <- cv_delta_se(
  attr_pars     = c("b_Habitat_QualityHigh", 
                    "b_Trail_ConditionHigh", 
                    "b_CrowdingLow"),
  cost_par      = "b_cost",
  model         = model_mxl,
  scenario_name = "High Improvement"
)

cv_results <- bind_rows(cv_medium_se, cv_high_se)

cat("\n═══════════════════════════════════════════════════════\n")
cat("CV Estimates with 95% Confidence Intervals\n")
cat("═══════════════════════════════════════════════════════\n")
print(cv_results)
cat("═══════════════════════════════════════════════════════\n")
```

```{r}
# ══════════════════════════════════════════════════════
# Step 7: Summary table 
# ══════════════════════════════════════════════════════
cat("\n═══════════════════════════════════════════════════════════\n")
cat("Welfare Summary Table\n")
cat("═══════════════════════════════════════════════════════════\n")
cat(sprintf("%-25s %10s %10s %12s\n", 
            "Scenario", "CV ($/trip)", "SE", "95% CI"))
cat(sprintf("%-25s %10s %10s %12s\n", 
            "Baseline", "$0.00", "—", "—"))
cat(sprintf("%-25s %10s %10s %12s\n",
            "Medium improvement",
            paste0("$", cv_results$CV[1]),
            paste0("$", cv_results$SE[1]),
            paste0("[$", cv_results$CI_low[1], 
                   ", $", cv_results$CI_high[1], "]")))
cat(sprintf("%-25s %10s %10s %12s\n",
            "High improvement",
            paste0("$", cv_results$CV[2]),
            paste0("$", cv_results$SE[2]),
            paste0("[$", cv_results$CI_low[2], 
                   ", $", cv_results$CI_high[2], "]")))
cat("═══════════════════════════════════════════════════════════\n")
cat("Note: CV = compensating variation per person per trip.\n")
cat("Positive values indicate welfare gains from improvement.\n")

# **What this gives you:**
# 
# - **CV Medium** — dollar value per person per trip of moving all attributes from baseline to medium improvement
# - **CV High** — dollar value per person per trip of moving all attributes from baseline to high improvement
# - **Standard errors and 95% CIs** via delta method
# - A clean summary table ready for your thesis
# 
# ---
# 
# **Next step after this runs:**
# 
# Once you have the per-person per-trip CV values, multiplying by visitor numbers gives you **aggregate welfare:**
# ```
# Total welfare = CV × annual trail visits × proportion resident/tourist

```
