---
title: "index"
format: html
editor: visual
---

```{r}
packageVersion("apollo")
library("apollo")
ls("package:apollo")


```

## MXL For All Respondents - Control viewpoint

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean=mlogit_clean[c(1:11,15,19,38:47, 71)]
mlogit_clean$Alternative[which(mlogit_clean$Alternative==1)]="alt1"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="2")]="alt2"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_wide=reshape(mlogit_clean,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))

#Interaction dummy for crowding with waterfall - Create combined indicator 
database$CrowdingAny.alt1 = database$CrowdingM.alt1 + database$CrowdingL.alt1
database$CrowdingAny.alt2 = database$CrowdingM.alt2 + database$CrowdingL.alt2
# Create interaction 
database$Crowding_WF.alt1 = database$CrowdingAny.alt1 * database$viewpoint
database$Crowding_WF.alt2 = database$CrowdingAny.alt2 * database$viewpoint


#Resident
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

# Apollo code

b_HHIncome_num = 0,

```{r}

apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  b_Crowding_WF         = 0, 

  # sociodems (fixed)
  b_resident  = 0,
  b_age       = 0,
  b_education = 0,
  b_income    = 0,
  b_sex       = 0,

  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)
apollo_fixed <- c()

```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  b_Crowding_WF           * Crowding_WF.alt1 +
  b_cost                  * Cost.alt1 +
  #b_viewpoint  * viewpoint +
  b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  b_Crowding_WF           * Crowding_WF.alt2 +
  b_cost                  * Cost.alt2 +
  #b_viewpoint  * viewpoint +
  b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = 0
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
model_mxl_crowd <- apollo_estimate(
  apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl)

```

```{r}

#Extract apollo model result 
est <- model_mxl_crowd $estimate

#Extract standard error
se <- sqrt(diag(model_mxl_crowd $robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_crowd_table <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

## **Crowd No Waterfall v Waterfall**

```{r}
database_trail <- database[database$viewpoint == 0, ]

database_wf <- database[database$viewpoint == 1, ]
```

```{r}
database <- database_wf
```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
model_trail <- apollo_estimate(
  apollo_beta,
  apollo_fixed,
  apollo_probabilities,
  apollo_inputs
)
```

```{r}

#Extract apollo model result 
est <- model_trail $estimate

#Extract standard error
se <- sqrt(diag(model_trail $robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_crowd.WF <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

## **Create Table: Combine output: Stargazer**

```{r}
# ── 0. Helper: extract estimates from apollo ──────────────────────────────────
get_apollo_stargazer_inputs <- function(model, robust = TRUE, p_sided = 2) {
  M  <- as.matrix(apollo_modelOutput(model,
                  modelOutput_settings = list(silent = TRUE)))
  b  <- M[, "Estimate"]
  if (robust) {
    se <- M[, "Rob.s.e."]
    t  <- M[, "Rob.t.rat.(0)"]
  } else {
    se <- M[, "s.e."]
    t  <- M[, "t.rat.(0)"]
  }
  p <- if (p_sided == 1) 1 - pnorm(abs(t)) else 2 * (1 - pnorm(abs(t)))
  names(b) <- names(se) <- names(p) <- rownames(M)
  list(b = b, se = se, p = p)
}

# ── 1. Helper: align coefficient vector to a fixed order ─────────────────────
align_to <- function(x, order) {
  out <- rep(NA_real_, length(order))
  names(out) <- order
  out[names(x)] <- x
  out
}

# ── 2. Extract from model ─────────────────────────────────────────────────────
v_all <- get_apollo_stargazer_inputs(model_mxl_crowd, robust = TRUE, p_sided = 2)

# ── 3. Coefficient order and display labels ───────────────────────────────────
order <- c(
  "b_Habitat_QualityMed",  "b_Habitat_QualityHigh",
  "b_Trail_ConditionMed",  "b_Trail_ConditionHigh",
  "b_CrowdingMed",         "b_CrowdingLow",
  "b_Crowding_WF",
  "b_cost",
  "b_resident",
  "b_age", "b_education", "b_income", "b_sex"
)

labels <- c(
  "Habitat quality (Medium)", "Habitat quality (High)",
  "Trail condition (Medium)", "Trail condition (High)",
  "Crowding (Medium)",        "Crowding (Low)",
  "Crowding \u00d7 Viewpoint",
  "Cost",
  "Resident",
  "Age", "Education", "Income", "Sex"
)

# ── 4. Align vectors ──────────────────────────────────────────────────────────
coef_list <- list(align_to(v_all$b,  order))
se_list   <- list(align_to(v_all$se, order))
p_list    <- list(align_to(v_all$p,  order))

# ── 5. Dummy OLS model ────────────────────────────────────────────────────────
make_dummy_lm_named <- function(coef_names, n = 100, seed = 1) {
  set.seed(seed)
  K <- length(coef_names)
  X <- as.data.frame(matrix(rnorm(n * K), nrow = n, ncol = K))
  names(X) <- coef_names
  X$y <- rnorm(n)
  lm(y ~ 0 + ., data = X)
}

d1 <- make_dummy_lm_named(order, seed = 1)

# ── 6. Model fit statistics ───────────────────────────────────────────────────
obs         <- model_mxl_crowd$nObs
respondents <- model_mxl_crowd$nIndivs
aic         <- round(model_mxl_crowd$AIC, 2)

# ── 7. Render table ───────────────────────────────────────────────────────────
stargazer(
  d1,
  type  = "html",
  out   = "mxl_crowd_robustness.html",
  title = "Mixed Logit Model — Crowding Context Robustness Test",
  column.labels          = c("All Respondents"),
  dep.var.labels.include = FALSE,
  covariate.labels       = labels,
  coef   = coef_list,
  se     = se_list,
  p      = p_list,
  digits    = 3,
  omit.stat = c("n", "f", "ser", "adj.rsq", "rsq"),
  add.lines = list(
    c("Observations",  obs),
    c("Respondents",   respondents),
    c("AIC",           aic)
  ),
  notes        = "Robust standard errors in parentheses.",
  notes.append = FALSE
)
```

## MXL For All Respondents - User group Test

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean=mlogit_clean[c(1:11,15,19,38:47, 71,74)]
mlogit_clean$Alternative[which(mlogit_clean$Alternative==1)]="alt1"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="2")]="alt2"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_wide=reshape(mlogit_clean,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
# # ── Step 1: Restrict to trail users only (using .alt1 version) ──
 database <- database[!is.na(database$HI_Trail.Use_Reason.alt1), ]

cat("Rows after dropping non-users:", nrow(database), "\n")
cat("Unique respondents:", length(unique(database$RID)), "\n")

# ── Step 2: Confirm factor levels ──
print(levels(database$HI_Trail.Use_Reason.alt1))

# ── Step 3: Create motivation dummies ──
database$Motiv_Social <- ifelse(
  database$HI_Trail.Use_Reason.alt1 == "Spending time with family / friends", 1, 0)

database$Motiv_Exercise <- ifelse(
  database$HI_Trail.Use_Reason.alt1 == "Exercise", 1, 0)

database$Motiv_Photography <- ifelse(
  database$HI_Trail.Use_Reason.alt1 == "Photography", 1, 0)

database$Motiv_Cultural <- ifelse(
  database$HI_Trail.Use_Reason.alt1 %in% c(
    "Cultural connection",
    "Collecting plants for cultural purposes"), 1, 0)

database$Motiv_Other <- ifelse(
  database$HI_Trail.Use_Reason.alt1 %in% c(
    "Hunting",
    "Other (Please enter answer in the box)"), 1, 0)

# ── Step 4: Verify counts ──
cat("\nMotivation dummy sums:\n")
print(colSums(database[, c("Motiv_Social", "Motiv_Exercise",
                            "Motiv_Photography", "Motiv_Cultural",
                            "Motiv_Other")], na.rm = TRUE))

cat("\nImplied Recreation rows (reference group):\n")
print(nrow(database) - sum(database$Motiv_Social + database$Motiv_Exercise +
                            database$Motiv_Photography + database$Motiv_Cultural +
                            database$Motiv_Other))

```

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))

#Interaction dummy for crowding with waterfall - Create combined indicator 
database$CrowdingAny.alt1 = database$CrowdingM.alt1 + database$CrowdingL.alt1
database$CrowdingAny.alt2 = database$CrowdingM.alt2 + database$CrowdingL.alt2
# Create interaction 
database$Crowding_WF.alt1 = database$CrowdingAny.alt1 * database$viewpoint
database$Crowding_WF.alt2 = database$CrowdingAny.alt2 * database$viewpoint


#Resident
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

# Apollo code

b_HHIncome_num = 0,

```{r}

# ──────────────────────────────────────────────
# BETA VECTOR
# ──────────────────────────────────────────────
apollo_beta <- c(
  # Means (random coefficients)
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0,

  # Original sociodemographic controls
  b_resident            = 0,
  b_age                 = 0,
  b_education           = 0,
  b_income              = 0,
  b_sex                 = 0,

  # Motivation main effects (Recreation = reference, omitted)
  b_Motiv_Social        = 0,
  b_Motiv_Exercise      = 0,
  b_Motiv_Photography   = 0,
  b_Motiv_Cultural      = 0,
  b_Motiv_Other         = 0,

  # Cost × Motivation interactions
  b_cost_Social         = 0,
  b_cost_Exercise       = 0,
  b_cost_Photography    = 0,
  b_cost_Cultural       = 0,
  b_cost_Other          = 0,

  # SDs for random coefficients
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)

apollo_fixed <- c()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs) {
  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed  * draw_Habitat_QualityMed
  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh
  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed  * draw_Trail_ConditionMed
  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh
  randcoeff[["b_CrowdingMed_R"]]         <- b_CrowdingMed +
    sd_CrowdingMed         * draw_CrowdingMed
  randcoeff[["b_CrowdingLow_R"]]         <- b_CrowdingLow +
    sd_CrowdingLow         * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_probabilities <- function(apollo_beta, apollo_inputs, functionality = "estimate") {

  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))

  P <- list()
  V <- list()

  # ── Effective cost coefficient (base + group deviation from Recreation) ──
  b_cost_eff <- b_cost +
    b_cost_Social      * Motiv_Social +
    b_cost_Exercise    * Motiv_Exercise +
    b_cost_Photography * Motiv_Photography +
    b_cost_Cultural    * Motiv_Cultural +
    b_cost_Other       * Motiv_Other

  # ── Sociodemographic + motivation shifter ──
  soc_dem <-
    b_resident           * Resident +
    b_age                * Demo_Age_num +
    b_education          * CollegePlus +
    b_income             * HHIncome_num +
    b_sex                * Sex_binary +
    b_Motiv_Social       * Motiv_Social +
    b_Motiv_Exercise     * Motiv_Exercise +
    b_Motiv_Photography  * Motiv_Photography +
    b_Motiv_Cultural     * Motiv_Cultural +
    b_Motiv_Other        * Motiv_Other

  # ── Utility: Alt 1 ──
  V[["alt1"]] <-
    b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
    b_CrowdingMed_R         * CrowdingM.alt1 +
    b_CrowdingLow_R         * CrowdingL.alt1 +
    b_cost_eff              * Cost.alt1 +
    soc_dem

  # ── Utility: Alt 2 ──
  V[["alt2"]] <-
    b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
    b_CrowdingMed_R         * CrowdingM.alt2 +
    b_CrowdingLow_R         * CrowdingL.alt2 +
    b_cost_eff              * Cost.alt2 +
    soc_dem

  # ── Utility: Alt 3 (opt-out) ──
  V[["alt3"]] <- asc_optout

  # ── MNL kernel → panel product → mix integration ──
  mnl_settings <- list(
    alternatives = c(alt1 = 1, alt2 = 2, alt3 = 3),
    avail        = list(alt1 = 1, alt2 = 1, alt3 = 1),
    choiceVar    = choice,
    utilities    = V
  )

  P[["model"]] <- apollo_mnl(mnl_settings, functionality)
  P <- apollo_panelProd(P, apollo_inputs, functionality)
  P <- apollo_avgInterDraws(P, apollo_inputs, functionality)
  P <- apollo_prepareProb(P, apollo_inputs, functionality)

  return(P)
}
```

```{r}
model_mxl_motiv <- apollo_estimate(
  apollo_beta,
  apollo_fixed,
  apollo_probabilities,
  apollo_inputs
)

summary(model_mxl_motiv)

```

```{r}

#Extract apollo model result 
est <- model_mxl_motiv $estimate

#Extract standard error
se <- sqrt(diag(model_mxl_motiv$robvarcov))

#Create coefficient table 
coef_table_motiv <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_crowd_table_motiv <- coef_table_motiv %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

## MXL For All Respondents - baseline model (restricted sample)

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean=mlogit_clean[c(1:11,15,19,38:47, 71,74)]
mlogit_clean$Alternative[which(mlogit_clean$Alternative==1)]="alt1"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="2")]="alt2"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_wide=reshape(mlogit_clean,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
# # ── Step 1: Restrict to trail users only (using .alt1 version) ──
 database <- database[!is.na(database$HI_Trail.Use_Reason.alt1), ]
```

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))

#Interaction dummy for crowding with waterfall - Create combined indicator 
database$CrowdingAny.alt1 = database$CrowdingM.alt1 + database$CrowdingL.alt1
database$CrowdingAny.alt2 = database$CrowdingM.alt2 + database$CrowdingL.alt2
# Create interaction 
database$Crowding_WF.alt1 = database$CrowdingAny.alt1 * database$viewpoint
database$Crowding_WF.alt2 = database$CrowdingAny.alt2 * database$viewpoint


#Resident
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

# Apollo code

b_HHIncome_num = 0,

```{r}

# ──────────────────────────────────────────────
# BETA VECTOR
# ──────────────────────────────────────────────
apollo_beta <- c(
  # Means (random coefficients)
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0,

  # Original sociodemographic controls
  b_resident            = 0,
  b_age                 = 0,
  b_education           = 0,
  b_income              = 0,
  b_sex                 = 0,

  # SDs for random coefficients
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)

apollo_fixed <- c()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs) {
  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed  * draw_Habitat_QualityMed
  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh
  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed  * draw_Trail_ConditionMed
  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh
  randcoeff[["b_CrowdingMed_R"]]         <- b_CrowdingMed +
    sd_CrowdingMed         * draw_CrowdingMed
  randcoeff[["b_CrowdingLow_R"]]         <- b_CrowdingLow +
    sd_CrowdingLow         * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  #b_Crowding_WF           * Crowding_WF.alt1 +
  b_cost                  * Cost.alt1 +
  #b_viewpoint  * viewpoint +
  b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  #b_Crowding_WF           * Crowding_WF.alt2 +
  b_cost                  * Cost.alt2 +
  #b_viewpoint  * viewpoint +
  b_resident   * Resident +
  b_age        * Demo_Age_num +
  b_education  * CollegePlus +
  b_income     * HHIncome_num +
  b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout 
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
model_mxl<- apollo_estimate(
  apollo_beta,
  apollo_fixed,
  apollo_probabilities,
  apollo_inputs
)

summary(model_mxl)

```

Likelihood Ratio test - Comparing orginal model (restricted to users who use trails) vs model with motivation/ reason of trail use

```{r}

# ── Step 2: Extract log-likelihoods ──
ll_base    <- model_mxl$LLout  # base model LL
ll_motiv   <- model_mxl_motiv$LLout            # motivation model LL

# ── Step 3: Degrees of freedom ──
# Number of additional parameters in motivation model:
# 5 main effects + 5 cost interactions = 10 new parameters
df_diff <- 10

# ── Step 4: LR test statistic ──
lr_stat <- -2 * (ll_base - ll_motiv)

# ── Step 5: p-value ──
p_val <- pchisq(lr_stat, df = df_diff, lower.tail = FALSE)

# ── Step 6: Print results ──
cat("═══════════════════════════════════════════\n")
cat("Likelihood Ratio Test\n")
cat("Base model (restricted sample) LL:", round(ll_base, 3), "\n")
cat("Motivation model LL:              ", round(ll_motiv, 3), "\n")
cat("LR statistic:                     ", round(lr_stat, 3), "\n")
cat("Degrees of freedom:               ", df_diff, "\n")
cat("p-value:                          ", round(p_val, 4), "\n")
cat("═══════════════════════════════════════════\n")

```

```{r}
# ── Step 7: AIC and BIC comparison (bonus) ──
# Penalizes for additional parameters — useful to report alongside LR test
n_obs <- 4940  # rows in restricted sample

aic_base  <- -2 * ll_base  + 2 * length(model_mxl$estimate)
aic_motiv <- -2 * ll_motiv + 2 * length(model_mxl_motiv$estimate)

bic_base  <- -2 * ll_base  + log(n_obs) * length(model_mxl$estimate)
bic_motiv <- -2 * ll_motiv + log(n_obs) * length(model_mxl_motiv$estimate)

cat("\nModel Fit Comparison:\n")
cat(sprintf("%-25s %10s %10s\n", "Metric", "Base", "Motivation"))
cat(sprintf("%-25s %10.3f %10.3f\n", "Log-likelihood", ll_base, ll_motiv))
cat(sprintf("%-25s %10.3f %10.3f\n", "AIC", aic_base, aic_motiv))
cat(sprintf("%-25s %10.3f %10.3f\n", "BIC", bic_base, bic_motiv))
cat(sprintf("%-25s %10d %10d\n", "Parameters", 
    length(model_mxl$estimate),
    length(model_mxl_motiv$estimate)))
```
