---
title: "Pilot overview"
author: "Valdo Viana & Ashley Lowe-Mckenzie"
date: "2025-11-03"
output: 
  html_document:
    code_folding: hide   # all code hidden by default, expandable
---

```{r setup, include=FALSE}
# Setup global chunk options
knitr::opts_chunk$set(
  echo = FALSE,       # hide code by default
  warning = FALSE,
  message = FALSE
)
```


```{r load-analysis, echo=FALSE}
source("3. Analysis/Analysis.R")
```

## Distribution of Levels by Attributes
```{r}
summary_data <- mlogit_clean %>%
  filter(Choice.Binary == 1) %>%       # only consider chosen alternatives
  distinct(RID, .keep_all = TRUE) %>%  # one row per respondent
  count(Zipverified, Trail_Condition) %>%         # count per cost per Zipverified
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  ) %>%
  ungroup()

ggplot(summary_data, aes(x = Trail_Condition, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  geom_text(aes(label = paste0("n=", n)),  
            position = position_dodge(0.9), 
            vjust = -0.5, size = 3) +       # add counts on top
  labs(
    title = "Distribution of Chosen Trail Conditions by Residency",
    x = "",
    y = "Proportion of times chosen"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 8),
    plot.title = element_text(size = 11, face = "bold")
  )
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  filter(Choice.Binary == 1) %>%       # only consider chosen alternatives
  distinct(RID, .keep_all = TRUE) %>%  # one row per respondent
  count(Zipverified, Habitat_Quality) %>%         # count per cost per Zipverified
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  ) %>%
  ungroup()

ggplot(summary_data, aes(x = Habitat_Quality, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  geom_text(aes(label = paste0("n=", n)), 
            position = position_dodge(0.9), 
            vjust = -0.5, size = 3) +       # add counts on top
  labs(
    title = "Distribution of Chosen Habitat Quality by Residency",
    x = "",
    y = "Proportion of times chosen"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 8),
    plot.title = element_text(size = 11, face = "bold")
  )
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
  filter(Choice.Binary == 1) %>%       # only consider chosen alternatives
  distinct(RID, .keep_all = TRUE) %>%  # one row per respondent
  count(Zipverified, Crowding) %>%         # count per cost per Zipverified
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  ) %>%
  ungroup()

ggplot(summary_data, aes(x = Crowding, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  geom_text(aes(label = paste0("n=", n)), 
            position = position_dodge(0.9), 
            vjust = -0.5, size = 3) +       # add counts on top
  labs(
    title = "Distribution of Chosen Crowding by Residency",
    x = "",
    y = "Proportion of times chosen"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 8),
    plot.title = element_text(size = 11, face = "bold")
  )
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
  filter(Choice.Binary == 1) %>%       # only consider chosen alternatives
  distinct(RID, .keep_all = TRUE) %>%  # one row per respondent
  count(Zipverified, Cost) %>%         # count per cost per Zipverified
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  ) %>%
  ungroup()

ggplot(summary_data, aes(x = Cost, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  geom_text(aes(label = paste0("n=", n)), 
            position = position_dodge(0.9), 
            vjust = -0.5, size = 3) +       # add counts on top
  labs(
    title = "Distribution of Chosen Cost by Residency",
    x = "",
    y = "Proportion of times chosen"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 8),
    plot.title = element_text(size = 11, face = "bold")
  )
rm(summary_data)
```


## User Fee Summary and Plot
```{r}

summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  group_by(Zipverified, User.fee_Y.N) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
    # se = sqrt(prop * (1 - prop) / total),   # standard error
    # ci_lower = (prop - 1.96 * se) * total,  # lower CI (optional)
    # ci_upper = (prop + 1.96 * se) * total   # upper CI (optional)
  )

ggplot(summary_data, aes(x = User.fee_Y.N, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  # geom_errorbar(
  #   aes(ymin = ci_lower, ymax = ci_upper),
  #   width = 0.2,
  #   position = position_dodge(0.9)
  # ) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Would you be willing to pay a user fee to support trail management efforts?",
    x = "",
    y = "Proportion of responses",
    fill = ""
  ) +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=8),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)

```

## Payment Type and Method 
```{r}

# Prepare summary with mean and 95% CI
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
    filter(User.fee_Payment.Type != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_Payment.Type) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
    # se = sqrt(prop * (1 - prop) / total),   # standard error
    # ci_lower = (prop - 1.96 * se) * total,  # lower CI (optional)
    # ci_upper = (prop + 1.96 * se) * total   # upper CI (optional)
  )

ggplot(summary_data, aes(x = User.fee_Payment.Type, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  # geom_errorbar(
  #   aes(ymin = ci_lower, ymax = ci_upper),
  #   width = 0.2,
  #   position = position_dodge(0.9)
  # ) +
    geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If user fees were implemented, which payment TYPE would you prefer?",
    x = "",
    y = "Proportion of responses",
    fill = ""
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=8),
         plot.title = element_text(size = 11, face = "bold"))

rm(summary_data)

summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_Payment.Method != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_Payment.Method) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_Payment.Method, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If user fees were implemented, which payment METHOD would you prefer?",
    x = "",
    y = "Proportion of responses",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=8),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_Natural.Features != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_Natural.Features) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_Natural.Features, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If User Fee is used on Trails with Natural Features (1 - Most Prefered & 5 - Least Prefered)
",
    x = "",
    y = "Proportions",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 10, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_High.Tourist != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_High.Tourist) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_High.Tourist, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If User Fee is used on Trails with High Tourist (1 - Most Prefered & 5 - Least Prefered)
",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 10, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_High.Maintance.Cost != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_High.Maintance.Cost) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_High.Maintance.Cost, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If User Fee is used on Trails with High Maintanance Cost (1 - Most Prefered & 5 - Least Prefered)
",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 10, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_Ecological.Sensitive != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_Ecological.Sensitive) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_Ecological.Sensitive, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If User Fee is used on Trails with High Ecological Sensitivity (1 - Most Prefered & 5 - Least Prefered)
",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 10, face = "bold"))
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(User.fee_Additional.Amenities != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, User.fee_Additional.Amenities) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = User.fee_Additional.Amenities, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If User Fee is used on Trails with Additional Ammenities (parking, restrooms) Sensitivity (1 - Most Preffered & 5 - Least Preffered)
",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 7.5, face = "bold"))
rm(summary_data)
```

## Cost Allocation 
```{r}

summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
   filter(Cost.Allocation != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Cost.Allocation) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
    # se = sqrt(prop * (1 - prop) / total),   # standard error
    # ci_lower = (prop - 1.96 * se) * total,  # lower CI (optional)
    # ci_upper = (prop + 1.96 * se) * total   # upper CI (optional)
  )

ggplot(summary_data, aes(x = Cost.Allocation, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +  # side-by-side bars
  # geom_errorbar(
  #   aes(ymin = ci_lower, ymax = ci_upper),
  #   width = 0.2,
  #   position = position_dodge(0.9)
  # ) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Who do you think should bear the majority of the cost for trail management?",
    x = "",
    y = "Proportion of responses",
    fill = ""
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=6),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)
```

## Certainty scale
```{r}

mean.CE <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified) %>%
summarise(mean_certainty = mean(Certainty.CE_Scale, na.rm = TRUE))

# Visualize Tourist vs Residents

mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
ggplot(aes(x = Certainty.CE_Scale, fill = Zipverified)) +
geom_histogram(binwidth = 1, color = "white", position = "dodge", boundary = 0.5) +
geom_vline(data = mean.CE,
aes(xintercept = mean_certainty, color = Zipverified),
linetype = "dashed", size = 1) +
scale_x_continuous(breaks = 1:10, limits = c(1, 11)) +
labs(
title = "Certainty Rankings of DCE Choices",
x = "Certainty Rank (1 = Lowest, 10 = Highest)",
y = "Number of Respondents",
fill = "Respondent Type",
color = "Mean Certainty"
) +
theme_minimal(base_size = 13) +
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=6),
         plot.title = element_text(size = 11, face = "bold")) +
scale_fill_manual(values = c("Resident" = "#4CAF50", "Tourist" = "#2196F3")) +
scale_color_manual(values = c("Resident" = "#2E7D32", "Tourist" = "#1565C0"))
rm(mean.CE)

```

## Management Choices (Full Image Attributes)
```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
filter(!is.na(Mgm.option_No.Text)) %>%
group_by(Zipverified, Mgm.option_No.Text) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Mgm.option_No.Text, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
    geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Management Choice Full Picture  (No Text)",
x = "",
y = "Proportion of Responses",
fill = ""
) +
theme_minimal() + 
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=8),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)

summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
filter(!is.na(Mgm.option_With.Text)) %>%
group_by(Zipverified, Mgm.option_With.Text) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Mgm.option_With.Text, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
    geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Management Choice Full Picture (With Text)",
x = "",
y = "Proportion of Responses",
fill = ""
) +
theme_minimal() + 
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=8),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)
```


## Likelihood of Using Trails with User Fee
```{r}
mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
ggplot(aes(x = Zipverified, y = Likelihood_Trail.Use, fill = Zipverified)) +
geom_boxplot() +
labs(
title = "Mean of Likelihood of Using Trails with User Fee (Boxplot) ",
x = "",
y = "Likelihood Rating (1–10)"
) +
theme_minimal() +
  theme(
    plot.title = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 9),
    legend.position = "none"
  )

summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified) %>%
summarise(
mean_rating = mean(Likelihood_Trail.Use, na.rm = TRUE),
sd_rating = sd(Likelihood_Trail.Use, na.rm = TRUE),
n = n(),
se = sd_rating / sqrt(n),
ci_lower = mean_rating - 1.96 * se,
ci_upper = mean_rating + 1.96 * se
)

ggplot(summary_data, aes(x = Zipverified, y = mean_rating, fill = Zipverified)) +
  geom_col(width = 0.5) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  geom_text(
    aes(label = sprintf("%.2f", mean_rating)),  # show mean rounded to 2 decimals
    vjust = -0.5,                               # position above the bar
    size = 2.5,                                 # smaller text
    color = "black"
  ) +
  labs(
    title = "Mean of Likelihood of Using Trails with User Fee (Bar Graph)",
    x = "",
    y = "Likelihood Rating (1–10)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 9),
    legend.position = "none"
  )
rm(summary_data)
```


### Self-Efficacy 

Self-efficacy, the belief in one's ability to succeed, directly influences behavior change by affecting whether a person will start a behavior, how much effort they will put in, and how long they will persist despite obstacles.


```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Self.Eff_UF_HQ != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Self.Eff_UF_HQ) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Self.Eff_UF_HQ, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Your contribution (via user fees) is making a meaningful difference on improving Habitat Quality (1-MOST confident & 3-LEAST confident)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0),
         plot.title = element_text(size = 7, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Self.Eff_UF_TC != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Self.Eff_UF_TC) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Self.Eff_UF_TC, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Your contribution (via user fees) is making a meaningful difference on improving Trail Condition (1-MOST confident & 3-LEAST confident)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 7, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Self.Eff_UF_Crowd != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Self.Eff_UF_Crowd) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Self.Eff_UF_Crowd, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Your contribution (via user fees) is making a meaningful difference on improving Crowding (1-MOST confident & 3-LEAST confident)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 7, face = "bold"))
rm(summary_data)
```

### Collective Efficacy
Collective efficacy drives behavior change by empowering groups to believe in their collective ability to achieve shared goals.


```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Collective.Eff_UF_HQ != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Collective.Eff_UF_HQ) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Collective.Eff_UF_HQ, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If most trail users choose to pay usage fees, do you think improvement on Habitat Quality would be addressed? (1-MOST addressed & 3-LEAST adressed)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 6.5, face = "bold"))
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Collective.Eff_UF_TC != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Collective.Eff_UF_TC) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Collective.Eff_UF_TC, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If most trail users choose to pay usage fees, do you think improvement on Trail Condition would be addressed? (1-MOST addressed & 3-LEAST adressed)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 6.5, face = "bold"))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Collective.Eff_UF_Crowd != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Collective.Eff_UF_Crowd) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Collective.Eff_UF_Crowd, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "If most trail users choose to pay usage fees, do you think improvement on Crowding would be addressed? (1-MOST addressed & 3-LEAST adressed)",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 6.5, face = "bold"))
rm(summary_data)
```


## Empirical Expectation 

Empirical expectation is a person's belief about what others are actually doing, and it significantly influences their own behavior change.

```{r}
mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
ggplot(aes(x = Zipverified, y = Empirical.Expec_Trail.Use, fill = Zipverified)) +
geom_boxplot() +
labs(
title = "Imagine 10 people you know—friends, family, coworkers. How many of them would be willing to use trails that require a user fee?",
x = "", y = ""
) +
theme_minimal() + 
  theme(
    plot.title = element_text(size = 7, face = "bold")
    )
```

## Normative Expectation

Normative expectation behavior change involves altering an individual's or group's actions by changing their beliefs about what is considered acceptable or typical behavior within a social group.
```{r}
mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
ggplot(aes(x = Zipverified, y = Normative.Expec_Trail.Use, fill = Zipverified)) +
geom_boxplot() +
labs(
title = "Imagine 10 people you know—friends, family, or coworkers. How many of them think that people should pay a user fee to use trails?",
x = "", y = ""
) +
theme_minimal() + 
  theme(
    plot.title = element_text(size = 7, face = "bold")
    )

```


## Support Volunteers and WTP 
```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified) %>%
summarise(
mean_rating = mean(Volunteer.WTP, na.rm = TRUE),
sd_rating = sd(Volunteer.WTP, na.rm = TRUE),
n = n(),
se = sd_rating / sqrt(n),
ci_lower = mean_rating - 1.96 * se,
ci_upper = mean_rating + 1.96 * se
)

ggplot(summary_data, aes(x = Zipverified, y = mean_rating, fill = Zipverified)) +
geom_col(width = 0.5) +
geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
labs(
title = "Average of WTP to Support Volunteers",
x = "Residency Status",
y = "Mean WTP (USD, one-time payment)"
) +
theme_minimal() + 
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=6),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)

summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
filter(!is.na(Volunteer.hours)) %>%
group_by(Zipverified, Volunteer.hours) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Volunteer.hours, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
    geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Number of hours willing to volunteer as a one-time contribution to support trail management",
x = "",
y = "Proportion of Responses",
fill = ""
) +
theme_minimal() + 
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=6),
         plot.title = element_text(size = 11, face = "bold"))
rm(summary_data)
```

### Survey Duration
```{r}
summary_time <- mlogit_clean %>%
summarise(
mean_time = mean(as.numeric(`Duration (in seconds)`), na.rm = TRUE) / 60,
sd_time = sd(as.numeric(`Duration (in seconds)`), na.rm = TRUE) / 60,
min_time = min(as.numeric(`Duration (in seconds)`), na.rm = TRUE) / 60,
max_time = max(as.numeric(`Duration (in seconds)`), na.rm = TRUE) / 60
)

kable(summary_time, caption = "Summary of Survey Duration (in minutes)")
```

# Demographic 

```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_Age) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_Age, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
      geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Age Distribution by Residency",
x = "",
y = "Proportion",
fill = "Residency"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
rm(summary_data)
```

```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_Education) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_Education, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
      geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Education Distribution by Residency",
x = "",
y = "Proportion",
fill = ""
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 15, hjust = 1, size = 4))
rm(summary_data)
```



```{r}

summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_Sex) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_Sex, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
      geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Sex Distribution by Residency",
x = "",
y = "Proportion",
fill = "Residency"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size = 10))
rm(summary_data)

```


```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_HH.Income) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_HH.Income, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Income Distribution by Residency",
x = "",
y = "Proportion",
fill = "Residency"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_Etnicity) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_Etnicity, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
        geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Ethnicity Distribution by Residency",
x = "",
y = "",
fill = "Residency"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 15, hjust = 1, size=5))
rm(summary_data)
```


```{r}
summary_data <- mlogit_clean %>%
distinct(RID, .keep_all = TRUE) %>%
group_by(Zipverified, Demo_Employment) %>%
summarise(n = n(), .groups = "drop") %>%
group_by(Zipverified) %>%
mutate(total = sum(n), prop = n / total)

ggplot(summary_data, aes(x = Demo_Employment, y = prop, fill = Zipverified)) +
geom_col(position = position_dodge(0.9)) +
        geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
labs(
title = "Employment Distribution by Residency",
x = "",
y = "",
fill = "Residency"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 15, hjust = 1, size=4))
rm(summary_data)
```


# Sanity Check   
 
```{r}

## Summarize block distribution 
summary_block.distribution <- merge.data.1 %>%
  distinct(RID, .keep_all = TRUE) %>% 
  group_by(Zipverified, block) %>% 
  count() %>% 
  group_by(Zipverified) %>% 
  mutate(percentage = n / sum(n) * 100)  # percentage within each Zipverified group

# Plot as bar chart with percentages
ggplot(summary_block.distribution, aes(x = block, y = percentage, fill = Zipverified)) +
  geom_col(position = "dodge") +  # side-by-side bars
  labs(
    title = "Distribution per Block by Residence Status",
    x = "Block",
    y = "Percentage (%)",
    fill = ""
  ) +
  theme_minimal() +
   theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=6),
         plot.title = element_text(size = 11, face = "bold"))

rm(summary_block.distribution)
```

```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Member_Env.Group != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Member_Env.Group) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Member_Env.Group, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "Are you currently a member of an environmental group / do you participate in environmental activities (e.g., volunteer for clean-up events)? ",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 6.5, face = "bold"))
rm(summary_data)
```
```{r}
summary_data <- mlogit_clean %>%
  distinct(RID, .keep_all = TRUE) %>%
  filter(Pay_Access.Fee != "Other (Please enter answer in the box)") %>%
  group_by(Zipverified, Pay_Access.Fee) %>%
  summarise(
    n = n(),  # count per alternative per Zipverified
    .groups = "drop"
  ) %>%
  group_by(Zipverified) %>%
  mutate(
    total = sum(n),       # total count within each Zipverified group
    prop = n / total      # proportion within Zipverified
  )

ggplot(summary_data, aes(x = Pay_Access.Fee, y = prop, fill = Zipverified)) +
  geom_col(position = position_dodge(0.9)) +
  geom_text(
    aes(label = paste0("n=", n)),   # use total from the same data
    position = position_dodge(0.9),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    title = "In the past 12 months, have you paid a fee to access a natural area (e.g., park entrance fee, trail permit)? ",
    x = "",
    y = "Proportion",
    fill = ""
  ) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
         plot.title = element_text(size = 7, face = "bold"))
rm(summary_data)
```


