---
title: "index"
format: html
editor: visual
---

```{r}
library(apollo)

apollo_initialise()

```

# MNL - RUM For All Respondents

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean=mlogit_clean[c(1:11,15,19,38:47, 71)]
mlogit_clean$Alternative[which(mlogit_clean$Alternative==1)]="alt1"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="2")]="alt2"
mlogit_clean$Alternative[which(mlogit_clean$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_wide=reshape(mlogit_clean,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#viewpoint
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))

#Resident 
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL - Apollo code

b_HHIncome_num = 0,

```{r}

apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0, 
  b_resident            = 0
  # b_age                 = 0,
  # b_education           = 0,
  #b_environment = 0, 
  #b_userfee = 0, 
  # b_income              = 0, 
  # b_sex = 0
)
apollo_fixed <- c()

```

```{r}

apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 +
    
    # person-specific covariates (shift alt1 vs opt-out)
    b_resident   * Resident 
    # b_age        * Demo_Age_num +
    # b_education  * CollegePlus +
    # #b_environment* Member.Environment_binary +
    # #b_userfee    * WTP_User.fee_binary +
    # b_income     * HHIncome_num +
    # b_sex        * Sex_binary
  
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 +
    
    # person-specific covariates (shift alt2 vs opt-out)
     b_resident   * Resident 
   #  b_age        * Demo_Age_num +
   #  b_education  * CollegePlus +
   #  #b_environment* Member.Environment_binary +
   # #b_userfee    * WTP_User.fee_binary +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary
   # 
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}

```

```{r}
model = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model)
```

```{r}

#Extract apollo model result 
est <- model$estimate

#Extract standard error
se <- sqrt(diag(model$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
coef_table <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# RUM For Trails (Residents Only)

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis


mlogit_clean_Residents=mlogit_clean_Residents[c(1:11,15,19,38:47, 71)]
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative==1)]="alt1"
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative=="2")]="alt2"
mlogit_clean_Residents$Alternative[which(mlogit_clean_Residents$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_Residents_wide=reshape(mlogit_clean_Residents,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_Residents_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL Resident - Apollo code

b_HHIncome_num = 0,

```{r}
apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout            = 0
  # b_age                 = 0,
  # b_education           = 0,
  # #b_environment = 0, 
  # b_income              = 0, 
  # b_sex = 0
)
apollo_fixed <- c()


apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 
    
    # person-specific covariates (shift alt1 vs opt-out)
   #  #b_resident   * Resident +
   #  b_age        * Demo_Age_num +
   #  b_education  * CollegePlus +
   # #b_environment* Member.Environment_binary +
   #  #b_userfee    * WTP_User.fee_binary +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary
   # 
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 
    
    # person-specific covariates (shift alt2 vs opt-out)
   # # b_resident   * Resident +
   #  b_age        * Demo_Age_num +
   #  b_education  * CollegePlus +
   #  #b_environment* Member.Environment_binary +
   # #b_userfee    * WTP_User.fee_binary +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}
```

```{r}
model_residents = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model_residents)
```

```{r}

# Extract Apollo model results
est.residents <- model_residents$estimate

# Extract standard errors
se.residents <- sqrt(diag(model_residents$robvarcov))

# Create coefficient table
coef_residents <- tibble(
  Parameter = names(est.residents),
  Estimate  = est.residents,
  SE        = se.residents[names(est.residents)]
)

# Add significance stars
coef_residents <- coef_residents %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# RUM For Trails (Tourists Only)

Here need to make the data into wide format to create the utility functions.

```{r}
#after running Analysis

mlogit_clean_Tourists=mlogit_clean_Tourists[c(1:11,15,19,38:47, 71)]
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative==1)]="alt1"
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative=="2")]="alt2"
mlogit_clean_Tourists$Alternative[which(mlogit_clean_Tourists$Alternative=="3")]="alt3"
#mlogit_clean$Choice.Binary=NULL
#Note design_ngene still says 50
# mlogit_clean$Cost[which(mlogit_clean$Cost==50)]=40
mlogit_clean_Tourists_wide=reshape(mlogit_clean_Tourists,timevar = "Alternative",
idvar = c(1:3,5,7),
direction = "wide" ) # Each respondent-choice task becomes one row, with separate columns for each alternative’s attributes.

apollo_control <- list(
  modelName  = "Trail_Choice",
  modelDescr = "Simple MNL model with trail alternatives",
  indivID    = "RID" ,
  panelData = TRUE
)
database=mlogit_clean_Tourists_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MNL Tourist Apollo code

b_HHIncome_num = 0,

```{r}

apollo_beta <- c(
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow        = 0,
  b_cost                = 0,
  asc_optout            = 0 
  # b_age                 = 0,
  # b_education           = 0,
  # #b_environment = 0, 
  # b_income              = 0, 
  # b_sex = 0
)
apollo_fixed <- c()


apollo_inputs<-apollo_validateInputs()
```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1
  V[["alt1"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt1 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt1 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt1 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt1 +
    b_CrowdingMed         * CrowdingM.alt1 +
    b_CrowdingLow         * CrowdingL.alt1 +
    b_cost                * Cost.alt1 
    
    # person-specific covariates (shift alt1 vs opt-out)
    #b_resident   * Resident +
   #  b_age        * Demo_Age_num +
   #  b_education  * CollegePlus +
   # #b_environment* Member.Environment_binary +
   #  #b_userfee    * WTP_User.fee_binary +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary
  
  # Utility for alt2
  V[["alt2"]]  =
    b_Habitat_QualityMed  * Habitat_QualityM.alt2 +
    b_Habitat_QualityHigh * Habitat_QualityH.alt2 +
    b_Trail_ConditionMed  * Trail_ConditionM.alt2 +
    b_Trail_ConditionHigh * Trail_ConditionH.alt2 +
    b_CrowdingMed         * CrowdingM.alt2 +
    b_CrowdingLow         * CrowdingL.alt2 +
    b_cost                * Cost.alt2 
    
    # person-specific covariates (shift alt2 vs opt-out)
   # b_resident   * Resident +
   #  b_age        * Demo_Age_num +
   #  b_education  * CollegePlus +
   #  #b_environment* Member.Environment_binary +
   # #b_userfee    * WTP_User.fee_binary +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary
   # 
  # Opt-out / status quo fixed at 0
  V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
  P[["model"]] = apollo_mnl(mnl_settings, functionality)
  P = apollo_panelProd(P, apollo_inputs, functionality)
  P = apollo_prepareProb(P, apollo_inputs, functionality)
  
  return(P)
}
```

```{r}
model_tourists = apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)

summary(model_tourists)
```

```{r}

# Extract Apollo model results
est.tourists <- model_tourists$estimate

# Extract standard errors
se.tourists<- sqrt(diag(model_tourists$robvarcov))

# Create coefficient table
coef_tourists <- tibble(
  Parameter = names(est.tourists),
  Estimate  = est.tourists,
  SE        = se.residents[names(est.tourists)]
)

# Add significance stars
coef_tourists <- coef_tourists%>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )

```

# MXL For All Respondents

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_wide
```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Crowding viewpoint
database %<>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))


#Resident 
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)


#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
# #Crowding with water fall 
#   b_CrowdingM_WF        = 0,
#   b_CrowdingL_WF        = 0,
  b_cost                = 0,
  asc_optout            = 0, 

  # # sociodems (fixed)
     b_resident  = 0,
  #   b_age       = 0,
  #   b_education = 0,
  #   b_income    = 0,
  #   b_sex       = 0,

  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1 
)
apollo_fixed <- c()

```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow
  

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
 # b_CrowdingM_WF           * CrowdingM_WF.alt1 + 
 # b_CrowdingL_WF          * CrowdingL_WF.alt1 +
  b_cost                  * Cost.alt1 +
  b_resident   * Resident 
  # b_age        * Demo_Age_num +
  # b_education  * CollegePlus +
  # b_income     * HHIncome_num +
  # b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
 # b_CrowdingM_WF           * CrowdingM_WF.alt2 + 
 # b_CrowdingL_WF          * CrowdingL_WF.alt2 +
   b_cost                  * Cost.alt2 +
    b_resident   * Resident 
   # b_age        * Demo_Age_num +
   # b_education  * CollegePlus +
   # b_income     * HHIncome_num +
   # b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
 # V[["alt3"]] = 0
    # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
model_mxl <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl)
```

```{r}

#Extract apollo model result 
est <- model_mxl$estimate

#Extract standard error
se <- sqrt(diag(model_mxl$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# MXL For Trails (Residents Only)

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_Residents_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout  = 0,   

  # sociodems (fixed)
   #b_resident  = 0,
   # b_age       = 0,
   # b_education = 0,
   # b_income    = 0,
   # b_sex       = 0,

  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)
apollo_fixed <- c()

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  b_cost                  * Cost.alt1 
 #b_resident   * Resident +
  # b_age        * Demo_Age_num +
  # b_education  * CollegePlus +
  # b_income     * HHIncome_num +
  # b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  b_cost                  * Cost.alt2 
   # #b_resident   * Resident +
   # b_age        * Demo_Age_num +
   # b_education  * CollegePlus +
   # b_income     * HHIncome_num +
   # b_sex        * Sex_binary
  
  # Opt-out / status quo fixed at 0
 # V[["alt3"]] = 0
    # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}
```

```{r}
model_mxl_Resident <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl_Resident)
```

```{r}

#Extract apollo model result 
est <- model_mxl_Resident$estimate

#Extract standard error
se <- sqrt(diag(model_mxl_Resident$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table_Resident <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# MXL For Trails (Tourist Only)

Here need to make the data into wide format to create the utility functions.

```{r}
database=mlogit_clean_Tourists_wide

```

To expand we will create for each alternative there is a low, medium, high for each alternative 1 and 2 . Alternative 3 is all zeros so we can deal with that in the utility function.

```{r}
database$Habitat_QualityL.alt1=0
database$Habitat_QualityL.alt1[which(database$Habitat_Quality.alt1=="Low")]=1
database$Habitat_QualityM.alt1=0
database$Habitat_QualityM.alt1[which(database$Habitat_Quality.alt1=="Medium")]=1
database$Habitat_QualityH.alt1=0
database$Habitat_QualityH.alt1[which(database$Habitat_Quality.alt1=="High")]=1

database$Habitat_QualityL.alt2=0
database$Habitat_QualityL.alt2[which(database$Habitat_Quality.alt2=="Low")]=1
database$Habitat_QualityM.alt2=0
database$Habitat_QualityM.alt2[which(database$Habitat_Quality.alt2=="Medium")]=1
database$Habitat_QualityH.alt2=0
database$Habitat_QualityH.alt2[which(database$Habitat_Quality.alt2=="High")]=1


database$Trail_ConditionL.alt1=0
database$Trail_ConditionL.alt1[which(database$Trail_Condition.alt1=="Low")]=1
database$Trail_ConditionM.alt1=0
database$Trail_ConditionM.alt1[which(database$Trail_Condition.alt1=="Medium")]=1
database$Trail_ConditionH.alt1=0
database$Trail_ConditionH.alt1[which(database$Trail_Condition.alt1=="High")]=1

database$Trail_ConditionL.alt2=0
database$Trail_ConditionL.alt2[which(database$Trail_Condition.alt2=="Low")]=1
database$Trail_ConditionM.alt2=0
database$Trail_ConditionM.alt2[which(database$Trail_Condition.alt2=="Medium")]=1
database$Trail_ConditionH.alt2=0
database$Trail_ConditionH.alt2[which(database$Trail_Condition.alt2=="High")]=1



## Crowding logic is reverse here when crowdings is coded at low it means there is high crowding when it is coded as high it means low crowding so here we reverse so that the one we drop is high crowding and compare what they would pay for medium or Low crowds.

database$CrowdingH.alt1=0
database$CrowdingH.alt1[which(database$Crowding.alt1=="Low")]=1
database$CrowdingM.alt1=0
database$CrowdingM.alt1[which(database$Crowding.alt1=="Medium")]=1
database$CrowdingL.alt1=0
database$CrowdingL.alt1[which(database$Crowding.alt1=="High")]=1



database$CrowdingH.alt2=0
database$CrowdingH.alt2[which(database$Crowding.alt2=="Low")]=1
database$CrowdingM.alt2=0
database$CrowdingM.alt2[which(database$Crowding.alt2=="Medium")]=1
database$CrowdingL.alt2=0
database$CrowdingL.alt2[which(database$Crowding.alt2=="High")]=1



```

Need to create some demographic info to control in the regression.

```{r}
database$Choice.Task.alt1


#Resident 
database <- database %>% mutate( viewpoint = if_else(as.numeric(Choice.Task.alt2) %%2 == 0,1,0))
database$Resident=0
database$Resident[which(database$Zipverified.alt1=="Resident")]=1

#Age
database$Demo_Age_num=as.integer(factor(
    database$Demo_Age.alt1,
    levels = c(
        "Under 18",
        "18-24 years old",
        "25-34 years old",
        "35-44 years old",
        "45-54 years old",
        "55-64 years old",
        "65+ years old"
    ),
    labels = 1:7
))

#Income 
database$HHIncome_num <- as.integer(factor(
  database$Demo_HH.Income.alt1,
  levels = c(
    "Less than $25,000",
    "$25,000 -$49,999",
    "$50,000 -$74,999",
    "$75,000 -$99,999",
    "$100,000 -$149,999",
    "$150,000 or more"
  ),
  labels = 1:6
))

#Education 
database$CollegePlus <- ifelse(
  database$Demo_Education.alt1 %in% c(
    "Bachelor's degree",
    "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)"
  ),
  1, 0
)

#member of environmental group
database$Member.Environment_binary <- ifelse(database$Member_Env.Group.alt1 == "Yes", 1, 0)
database$WTP_User.fee_binary       <- ifelse(database$User.fee_Y.N.alt1      == "Yes", 1, 0)
database$Sex_binary <- ifelse(database$Demo_Sex.alt1=="Female", 1,
                             ifelse(database$Demo_Sex.alt1=="Male", 0, NA))
database$Sex_binary[is.na(database$Sex_binary)] <- 0   # if you still want to force it

database$Resident                  <- ifelse(database$Zipverified.alt1       == "Resident", 1, 0)


#database=database[c(1,3,4,6,10,11:18,28,46, 55:81)]
colnames(database)[1]="RID"
colnames(database)[4]="choice"

database$choice=as.numeric(
  database$choice
)
database$choice=as.numeric(database$choice)
```

## MXL - Apollo code

```{r}
apollo_beta <- c(
  # means
  b_Habitat_QualityMed  = 0,
  b_Habitat_QualityHigh = 0,
  b_Trail_ConditionMed  = 0,
  b_Trail_ConditionHigh = 0,
  b_CrowdingMed         = 0,
  b_CrowdingLow         = 0,
  b_cost                = 0,
  asc_optout = 0,

  # sociodems (fixed)
  #b_resident  = 0,
    # b_age       = 0,
    # b_education = 0,
    # b_income    = 0,
    # b_sex       = 0,


  # SDs for random coeffs (start close to zero but allow heterogeneity to grow if the data support it)
  sd_Habitat_QualityMed  = 0.1,
  sd_Habitat_QualityHigh = 0.1,
  sd_Trail_ConditionMed  = 0.1,
  sd_Trail_ConditionHigh = 0.1,
  sd_CrowdingMed         = 0.1,
  sd_CrowdingLow         = 0.1
)
apollo_fixed <- c()

```

```{r}
apollo_inputs <- apollo_validateInputs()
```

```{r}
apollo_draws <- list(
  interDrawsType = "halton",
  interNDraws    = 500,     # start with 200–500; increase later
  interNormDraws = c(
    "draw_Habitat_QualityMed",
    "draw_Habitat_QualityHigh",
    "draw_Trail_ConditionMed",
    "draw_Trail_ConditionHigh",
    "draw_CrowdingMed",
    "draw_CrowdingLow"
  )
)

apollo_randCoeff <- function(apollo_beta, apollo_inputs){

  randcoeff <- list()

  randcoeff[["b_Habitat_QualityMed_R"]]  <- b_Habitat_QualityMed +
    sd_Habitat_QualityMed * draw_Habitat_QualityMed

  randcoeff[["b_Habitat_QualityHigh_R"]] <- b_Habitat_QualityHigh +
    sd_Habitat_QualityHigh * draw_Habitat_QualityHigh

  randcoeff[["b_Trail_ConditionMed_R"]]  <- b_Trail_ConditionMed +
    sd_Trail_ConditionMed * draw_Trail_ConditionMed

  randcoeff[["b_Trail_ConditionHigh_R"]] <- b_Trail_ConditionHigh +
    sd_Trail_ConditionHigh * draw_Trail_ConditionHigh

  randcoeff[["b_CrowdingMed_R"]] <- b_CrowdingMed +
    sd_CrowdingMed * draw_CrowdingMed

  randcoeff[["b_CrowdingLow_R"]] <- b_CrowdingLow +
    sd_CrowdingLow * draw_CrowdingLow

  return(randcoeff)
}

```

```{r}
apollo_probabilities=function(apollo_beta, apollo_inputs, functionality="estimate"){
  
  apollo_attach(apollo_beta, apollo_inputs)
  on.exit(apollo_detach(apollo_beta, apollo_inputs))
  
  P = list()
  V = list()
  
  # Utility for alt1

V[["alt1"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt1 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt1 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt1 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt1 +
  b_CrowdingMed_R         * CrowdingM.alt1 +
  b_CrowdingLow_R         * CrowdingL.alt1 +
  b_cost                  * Cost.alt1 
  # # #b_resident   * Resident +
   #  b_age        * Demo_Age_num +
   # b_education  * CollegePlus +
   #  b_income     * HHIncome_num +
   #  b_sex        * Sex_binary

  
  # Utility for alt2
  V[["alt2"]]  =
  b_Habitat_QualityMed_R  * Habitat_QualityM.alt2 +
  b_Habitat_QualityHigh_R * Habitat_QualityH.alt2 +
  b_Trail_ConditionMed_R  * Trail_ConditionM.alt2 +
  b_Trail_ConditionHigh_R * Trail_ConditionH.alt2 +
  b_CrowdingMed_R         * CrowdingM.alt2 +
  b_CrowdingLow_R         * CrowdingL.alt2 +
  b_cost                  * Cost.alt2 
  # #b_resident   * Resident +
    # b_age        * Demo_Age_num +
    # b_education  * CollegePlus +
    # b_income     * HHIncome_num +
    # b_sex        * Sex_binary
   
  # utility for alt 3 
V[["alt3"]] = asc_optout
  
  mnl_settings = list(
    alternatives  = c(alt1=1, alt2=2, alt3=3),
    avail         = list(alt1=1, alt2=1, alt3=1),
    choiceVar     = choice,
    utilities     = V
  )
  
P[["model"]] = apollo_mnl(mnl_settings, functionality)

P = apollo_panelProd(P, apollo_inputs, functionality)

P = apollo_avgInterDraws(P, apollo_inputs, functionality)  # <-- mixed logit integration  

P = apollo_prepareProb(P, apollo_inputs, functionality)

  
  return(P)
}

```

```{r}
model_mxl_Tourist <- apollo_estimate(apollo_beta, apollo_fixed, apollo_probabilities, apollo_inputs)
summary(model_mxl_Tourist)
```

```{r}

#Extract apollo model result 
est <- model_mxl_Tourist$estimate

#Extract standard error
se <- sqrt(diag(model_mxl_Tourist$robvarcov))

#Create coefficient table 
coef_table <- tibble(
  Parameter = names(est),
  Estimate  = est,
  SE        = se[names(est)]
)

#Add significance stars
MXL_coef_table_Tourist <- coef_table %>%
  mutate(
    z = Estimate / SE,
    Stars = case_when(
      abs(z) > 3.29 ~ "***",
      abs(z) > 2.58 ~ "**",
      abs(z) > 1.96 ~ "*",
      TRUE ~ ""
    )
  )
```

# **Create Utility Table: Combine output: Stargazer**

```{r}
get_apollo_stargazer_inputs <- function(model, robust = TRUE, p_sided = 2) {
  M <- as.matrix(apollo_modelOutput(model, modelOutput_settings = list(silent = TRUE)))

  b <- M[, "Estimate"]

  if (robust) {
    se <- M[, "Rob.s.e."]
    t  <- M[, "Rob.t.rat.(0)"]
  } else {
    se <- M[, "s.e."]
    t  <- M[, "t.rat.(0)"]
  }

  # p-values from t-ratio (normal approximation)
  if (p_sided == 1) {
    p <- 1 - pnorm(abs(t))             # 1-sided
  } else {
    p <- 2 * (1 - pnorm(abs(t)))       # 2-sided
  }

  names(b)  <- rownames(M)
  names(se) <- rownames(M)
  names(p)  <- rownames(M)

  list(b = b, se = se, p = p)
}

align_to <- function(x, order) {
  out <- rep(NA_real_, length(order))
  names(out) <- order
  out[names(x)] <- x
  out
}

make_dummy_lm_named <- function(coef_names, n = 100, seed = 1) {
  set.seed(seed)
  K <- length(coef_names)
  X <- as.data.frame(matrix(rnorm(n * K), nrow = n, ncol = K))
  names(X) <- coef_names
  X$y <- rnorm(n)
  lm(y ~ 0 + ., data = X)  # no intercept
}
```

```{r}
#library(stargazer)

# Extract
v_MNL_all  <- get_apollo_stargazer_inputs(model,      robust = TRUE, p_sided = 2)
v_MNL_res  <- get_apollo_stargazer_inputs(model_residents, robust = TRUE, p_sided = 2)
v_MNL_tour <- get_apollo_stargazer_inputs(model_tourists,  robust = TRUE, p_sided = 2)
v_MXL_all  <- get_apollo_stargazer_inputs(model_mxl,      robust = TRUE, p_sided = 2)
v_MXL_res  <- get_apollo_stargazer_inputs(model_mxl_Resident, robust = TRUE, p_sided = 2)
v_MXL_tour <- get_apollo_stargazer_inputs(model_mxl_Tourist,  robust = TRUE, p_sided = 2)

# Choose your row order (edit if needed)
order <- c(
  "b_Habitat_QualityMed","b_Habitat_QualityHigh",
  "b_Trail_ConditionMed","b_Trail_ConditionHigh",
  "b_CrowdingMed","b_CrowdingLow", "asc_optout",
  "b_cost",
  "b_resident",


  "sd_Habitat_QualityMed","sd_Habitat_QualityHigh",
  "sd_Trail_ConditionMed","sd_Trail_ConditionHigh",
  "sd_CrowdingMed","sd_CrowdingLow"
)


labels <- c(
  "Habitat quality (Medium)","Habitat quality (High)",
  "Trail condition (Medium)","Trail condition (High)",
  "Crowding (Medium)","Crowding (Low)","ASC",
  "Cost",
  "Resident",
  "SD: Habitat quality (Medium)","SD: Habitat quality (High)",
  "SD: Trail condition (Medium)","SD: Trail condition (High)",
  "SD: Crowding (Medium)","SD: Crowding (Low)"
)


# Align each model’s vectors to the same coefficient list
coef_list <- list(
  align_to(v_MNL_all$b,  order),
  align_to(v_MNL_res$b,  order),
  align_to(v_MNL_tour$b, order),
  align_to(v_MXL_all$b,  order),
  align_to(v_MXL_res$b,  order),
  align_to(v_MXL_tour$b, order)
)

se_list <- list(
  align_to(v_MNL_all$se,  order),
  align_to(v_MNL_res$se,  order),
  align_to(v_MNL_tour$se, order),
  align_to(v_MXL_all$se,  order),
  align_to(v_MXL_res$se,  order),
  align_to(v_MXL_tour$se, order)
)

p_list <- list(
  align_to(v_MNL_all$p,  order),
  align_to(v_MNL_res$p,  order),
  align_to(v_MNL_tour$p, order),
  align_to(v_MXL_all$p,  order),
  align_to(v_MXL_res$p,  order),
  align_to(v_MXL_tour$p, order)
)

# Dummy models for stargazer
make_dummy_lm_named <- function(coef_names, n = 100, seed = 1) {
  set.seed(seed)
  K <- length(coef_names)
  X <- as.data.frame(matrix(rnorm(n * K), nrow = n, ncol = K))
  names(X) <- coef_names
  X$y <- rnorm(n)
  lm(y ~ 0 + ., data = X)  # no intercept, so exactly K coefs with these names
}

d1 <- make_dummy_lm_named(order, seed = 1)
d2 <- make_dummy_lm_named(order, seed = 2)
d3 <- make_dummy_lm_named(order, seed = 3)
d4 <- make_dummy_lm_named(order, seed = 4)
d5 <- make_dummy_lm_named(order, seed = 5)
d6 <- make_dummy_lm_named(order, seed = 6)



```

```{r}
obs <- c(model$nObs, model_residents$nObs, model_tourists$nObs,
         model_mxl$nObs, model_mxl_Resident$nObs, model_mxl_Tourist$nObs)

resp <- c(model$nIndivs, model_residents$nIndivs, model_tourists$nIndivs,
          model_mxl$nIndivs, model_mxl_Resident$nIndivs, model_mxl_Tourist$nIndivs)

aic <- round(c(model$AIC, model_residents$AIC, model_tourists$AIC,
               model_mxl$AIC, model_mxl_Resident$AIC, model_mxl_Tourist$AIC), 2)

ll  <- round(c(model$LLout, model_residents$LLout, model_tourists$LLout,
                model_mxl$LLout, model_mxl_Resident$LLout, model_mxl_Tourist$LLout), 2)

bic <- round(c(model$BIC, model_residents$BIC, model_tourists$BIC,
                model_mxl$BIC, model_mxl_Resident$BIC, model_mxl_Tourist$BIC), 2)



```

```{r}
#Combined MXL and MNL 

stargazer(
 d1, d2, d3, d4, d5, d6, 
  type = "html",
  out  = "Mnl_Mxl_table_No_Demo.html",
  title = "Trail Choice Model Results with No Demographics",

  column.labels   = c("MNL", "MXL"),
  column.separate = c(3, 3),

  model.numbers = TRUE,            # shows (1)-(6)
  dep.var.labels.include = FALSE,

  covariate.labels = labels,
  coef = coef_list, se = se_list, p = p_list,
  omit.stat = c("n","f","ser","adj.rsq","rsq"),
  add.lines = list(
    c("Observations", obs),
    c("Respondents",  resp),
    c("Log-likelihood", ll),
    c("AIC", aic),
    c("BIC", bic)
  ),
  notes = "Columns (1)-(3): All / Residents / Tourists (MNL). Columns (4)-(6): All / Residents / Tourists (MXL). SE in parentheses.",
  notes.append = FALSE
)




```

```{r}
#Only MNL model 
stargazer(
  d1, d2, d3,
  type = "html",
  out  = "MNL_No_Demo.html",
  title = "Multinomial Logit Model Results",

  model.numbers = FALSE,
  dep.var.labels.include = FALSE,

  column.labels = c("All respondents", "Residents", "Tourists"),
  column.separate = c(1,1,1),

  covariate.labels = labels,

  coef = coef_list[1:3],
  se   = se_list[1:3],
  p    = p_list[1:3],

  omit.stat = c("n","f","ser","adj.rsq","rsq"),

  add.lines = list(
    c("Observations", obs[1:3]),
    c("Respondents",  resp[1:3]),
    c("Log-likelihood", ll),
    c("AIC", aic),
    c("BIC", bic)
  ),

  notes = "Robust standard errors in parentheses.",
  notes.append = FALSE
)

```

```{r}
#Only MXL model 
stargazer(
  d4, d5, d6,
  type = "html",
  out  = "MXL_No_Demo.html",
  title = "Mixed Logit (MXL) Model Results with No Demographics",

  model.numbers = FALSE,
  dep.var.labels.include = FALSE,

  column.labels = c("All respondents", "Residents", "Tourists"),
  column.separate = c(1,1,1),

  covariate.labels = labels,

  coef = coef_list[4:6],
  se   = se_list[4:6],
  p    = p_list[4:6],

  omit.stat = c("n","f","ser","adj.rsq","rsq"),

  add.lines = list(
    c("Observations", obs[4:6]),
    c("Respondents",  resp[4:6]),
    c("Log-likelihood", ll[4:6]),
    c("AIC", aic[4:6]),
    c("BIC", bic[4:6])
  ),

  notes = "Robust standard errors in parentheses.",
  notes.append = FALSE
)
```

```{r}
#Only MXL model (column number)
stargazer(
  d4, d5, d6,
  type = "html",
  out  = "MXL_table2.html",
  title = "Mixed Logit (MXL) Model Results",

  model.numbers = TRUE,
  dep.var.labels.include = FALSE,

  column.labels = c("All respondents", "Residents", "Tourists"),
  column.separate = c(1,1,1),

  covariate.labels = labels,

  coef = coef_list[4:6],
  se   = se_list[4:6],
  p    = p_list[4:6],

  omit.stat = c("n","f","ser","adj.rsq","rsq"),

  add.lines = list(
    c("Observations", obs[4:6]),
    c("Respondents",  resp[4:6]),
    c("AIC",          aic[4:6])
  ),
  notes.append = FALSE
)
```

# WTP Mean

```{r}

# Attributes you want WTP for (these are the *mean* taste parameters)
wtp_pars <- c(
  "b_Habitat_QualityMed",
  "b_Habitat_QualityHigh",
  "b_Trail_ConditionMed",
  "b_Trail_ConditionHigh",
  "b_CrowdingMed",
  "b_CrowdingLow"
)

cost_par <- "b_cost"   # <- fixed cost coefficient name in the fixed-cost model

```

```{r}
wtp_delta <- function(model, wtp_pars, cost_par = "b_cost", use_robust = TRUE){
  bhat <- model$estimate
  Vhat <- if(use_robust) (model$robvarcov %||% model$varcov) else model$varcov
  if(is.null(Vhat)) stop("No varcov/robvarcov found in model object.")

  needed <- c(wtp_pars, cost_par)
  missing <- setdiff(needed, names(bhat))
  if(length(missing) > 0) stop("Missing parameters in model$estimate: ", paste(missing, collapse=", "))

  bc <- as.numeric(bhat[cost_par])
  if(is.na(bc)) stop("Cost parameter not found.")

  out <- lapply(wtp_pars, function(p){
    bk <- as.numeric(bhat[p])

    wtp <- -bk / bc

    # gradient vector aligned to (bk, bc)
    g <- c(d_bk = -1/bc,
           d_bc =  bk/(bc^2))

    # extract 2x2 varcov for (bk, bc)
    V2 <- as.matrix(Vhat[c(p, cost_par), c(p, cost_par)])

    var_wtp <- as.numeric(t(g) %*% V2 %*% g)
    se_wtp  <- sqrt(var_wtp)

    tibble(
      Attribute = p,
      wtp = wtp,
      lo95 = wtp - 1.96 * se_wtp,
      hi95 = wtp + 1.96 * se_wtp
    )
  })

  bind_rows(out)
}

```

```{r}
# wtp_krinsky_robb <- function(model, wtp_pars, cost_par="b_cost",
#                              R = 20000, use_robust = TRUE, seed = 123){
#   set.seed(seed)
# 
#   bhat <- model$estimate
#   Vhat <- if(use_robust) (model$robvarcov %||% model$varcov) else model$varcov
#   if(is.null(Vhat)) stop("No varcov/robvarcov found in model object.")
# 
#   needed <- c(wtp_pars, cost_par)
#   missing <- setdiff(needed, names(bhat))
#   if(length(missing) > 0) stop("Missing parameters in model$estimate: ", paste(missing, collapse=", "))
# 
#   # Work on the subset vector (wtp_pars + cost_par)
#   pars <- c(wtp_pars, cost_par)
#   mu   <- as.numeric(bhat[pars])
#   Sig  <- as.matrix(Vhat[pars, pars])
# 
#   draws <- MASS::mvrnorm(n = R, mu = mu, Sigma = Sig)
#   colnames(draws) <- pars
# 
#   bc_draw <- draws[, cost_par]
# 
#   # WTP draws for each attribute
#   wtp_draws <- sapply(wtp_pars, function(p){
#     -draws[, p] / bc_draw
#   })
#   colnames(wtp_draws) <- wtp_pars
# 
#   # Point estimate from bhat (same formula)
#   bc <- as.numeric(bhat[cost_par])
# 
#   tibble(
#     Attribute = wtp_pars,
#     wtp  = -as.numeric(bhat[wtp_pars]) / bc,
#     lo95 = apply(wtp_draws, 2, quantile, 0.025, na.rm=TRUE),
#     hi95 = apply(wtp_draws, 2, quantile, 0.975, na.rm=TRUE)
#   )
# }

```

```{r}
# wtp_all  <- wtp_krinsky_robb(model_mxl,  wtp_pars, cost_par, R=20000, seed=1)
# wtp_res  <- wtp_krinsky_robb(model_mxl_Resident,  wtp_pars, cost_par, R=20000, seed=2)
# wtp_tour <- wtp_krinsky_robb(model_mxl_Tourist, wtp_pars, cost_par, R=20000, seed=3)


```

```{r}
 wtp_all_delta  <- wtp_delta(model_mxl, wtp_pars, cost_par)
 wtp_res_delta  <- wtp_delta(model_mxl_Resident,  wtp_pars, cost_par)
 wtp_tour_delta<- wtp_delta(model_mxl_Tourist, wtp_pars, cost_par)

```

```{r}
# fmt_cell <- function(est, lo, hi, digits=2){
#   sprintf(paste0("%.",digits,"f (%.",digits,"f\u2013%.",digits,"f)"), est, lo, hi)
# }
# 
# order_pars <- wtp_pars
# row_labels <- c(
#   "Habitat Quality: Medium",
#   "Habitat Quality: High",
#   "Trail Condition: Medium",
#   "Trail Condition: High",
#   "Crowding: Medium",
#   "Crowding: Low"
# )
# 
# prep_col <- function(df){
#   df <- df[match(order_pars, df$Attribute), ]
#   mapply(fmt_cell, df$wtp, df$lo95, df$hi95, MoreArgs=list(digits=2))
# }
# 
# wtp_table <- data.frame(
#   `Attributes` = row_labels,
#   `All respondents` = prep_col(wtp_all_delta),
#   `Residents`       = prep_col(wtp_res_delta),
#   `Tourists`        = prep_col(wtp_tour_delta),
#   check.names = FALSE
# )

# stargazer(wtp_table,
#           summary = FALSE,
#           rownames = FALSE,
#           title = "Willingness to pay per entrance for trail improvements across groups.",
#           notes = "95% confidence intervals in parentheses",
#           type = "text")

```

```{r}
# stargazer(
#   wtp_table,
#   summary = FALSE,
#   rownames = FALSE,
#   title = "Willingness to pay per trip for trail improvements across groups.",
#   notes = "95% confidence intervals in parentheses.",
#   type = "html",
#   out  = "WTP_table.html"
# )

```

```{r}
# First, let's get the data in the right format
order_pars <- wtp_pars
row_labels <- c(
  "Habitat Quality: Medium",
  "Habitat Quality: High",
  "Trail Condition: Medium", 
  "Trail Condition: High",
  "Crowding: Medium",
  "Crowding: Low"
)

# Create a function to prepare data for stargazer with two rows per attribute
create_stargazer_data <- function(wtp_all, wtp_res, wtp_tour) {
  # Reorder to match the desired order
  wtp_all <- wtp_all[match(order_pars, wtp_all$Attribute), ]
  wtp_res <- wtp_res[match(order_pars, wtp_res$Attribute), ]
  wtp_tour <- wtp_tour[match(order_pars, wtp_tour$Attribute), ]
  
  # Initialize vectors for the table
  attributes_col <- character()
  all_resp_col <- character()
  residents_col <- character()
  tourists_col <- character()
  
  # For each attribute, add two rows: one for mean, one for CI
for(i in 1:nrow(wtp_all)) {
    # Row 1: Mean value
attributes_col <- c(attributes_col, row_labels[i])
all_resp_col   <- c(all_resp_col,  sprintf("DOLLARSIGN%.0f", wtp_all$wtp[i]))
residents_col  <- c(residents_col, sprintf("DOLLARSIGN%.0f", wtp_res$wtp[i]))
tourists_col   <- c(tourists_col,  sprintf("DOLLARSIGN%.0f", wtp_tour$wtp[i]))


    # Row 2: Confidence interval
    attributes_col <- c(attributes_col, "")
    all_resp_col <- c(all_resp_col, sprintf("(%.0f\u2013%.0f)", wtp_all$lo95[i], wtp_all$hi95[i]))
    residents_col <- c(residents_col, sprintf("(%.0f\u2013%.0f)", wtp_res$lo95[i], wtp_res$hi95[i]))
    tourists_col <- c(tourists_col, sprintf("(%.0f\u2013%.0f)", wtp_tour$lo95[i], wtp_tour$hi95[i]))
  }
  
  # Create the data frame
  data.frame(
    Attributes = attributes_col,
    `All respondents` = all_resp_col,
    Residents = residents_col,
    Tourists = tourists_col,
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
}

```

```{r}
# Create the table data
stargazer_data <- create_stargazer_data(wtp_all_delta, wtp_res_delta, wtp_tour_delta)

# Rename columns to include numbers
colnames(stargazer_data) <- c(
  "Attribute",
  "All respondents<br/>(1)",
  "Residents<br/>(2)",
  "Tourists<br/>(3)"
)

# Create the table with stargazer
stargazer(
  stargazer_data,
  summary = FALSE,
  rownames = FALSE,
  title = "Willingness to pay per use for trail improvements across groups.",
  notes = "95% confidence intervals in parentheses.",
  type = "html",
  out = "WTP_table.CI.html",
  # Add styling to improve appearance
  column.sep.width = "10pt",
  font.size = "small",
  # Remove default note about number of observations
  notes.align = "l",
  notes.append = FALSE
)

# Then replace the placeholder with $ in the output file
html_content <- readLines("WTP_table.CI.html")
html_content <- gsub("DOLLARSIGN", "$", html_content, fixed = TRUE)
html_content <- gsub("< br/> ", "<br/>", html_content, fixed = TRUE)
writeLines(html_content, "WTP_table.CI.html")
```

# WTP Graph: TC and HQ

```{r}
# --- Step 1: Create Attribute level table 
attr_levels <- data.frame(
  Attribute = c("b_Habitat_QualityMed", "b_Habitat_QualityHigh", "b_Trail_ConditionMed", "b_Trail_ConditionHigh"),
  AttributeName = c("Habitat Quality", "Habitat Quality", "Trail Condition", "Trail Condition"),
  Level = c("Medium", "High", "Medium", "High"),
  stringsAsFactors = FALSE
)

wtp_all  <- wtp_all_delta  %>% mutate(Group = "All respondents")
wtp_res  <- wtp_res_delta  %>% mutate(Group = "Residents")
wtp_tour <- wtp_tour_delta %>% mutate(Group = "Tourists")

wtp_combined <- bind_rows(wtp_all, wtp_res, wtp_tour) %>%
  right_join(attr_levels, by = "Attribute")

# --- Step 2: Build gap annotation data (Tourists minus Residents, at "High" level)
gap_data <- wtp_combined %>%
  filter(Group %in% c("Residents", "Tourists")) %>%
  select(AttributeName, Level, Group, wtp) %>%
  pivot_wider(names_from = Group, values_from = wtp) %>%33
  mutate(
    gap = round(Tourists - Residents),        # rounded difference
    label = paste0("+$", gap)                 # label e.g. "+$52"
  )

group_colors <- c("All respondents" = "grey", "Residents" = "#6a906c", "Tourists" = "#ae9864")

p <- ggplot(wtp_combined, aes(x = Level, y = wtp, color = Group, group = Group)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  # Rounded value labels above points
  geom_text(aes(label = paste0("$", round(wtp))),
            vjust = -0.8,
            size = 3,
            show.legend = FALSE,
            fontface = "bold",
            color = "black") +
  # # Gap bracket: vertical segment between Residents and Tourists
  # geom_segment(
  #   data = gap_data,
  #   aes(x = Level, xend = Level,
  #       y = Residents, yend = Tourists),
  #   inherit.aes = FALSE,
  #   color = "black",
  #   linewidth = 0.6,
  #   linetype = "dashed",
  #   arrow = arrow(ends = "both", length = unit(0.15, "cm"), type = "closed")
  # ) +
  # # Gap label to the right of the bracket
  # geom_text(
  #   data = gap_data,
  #   aes(x = Level,
  #       y = (Residents + Tourists) / 2,
  #       label = label),
  #   inherit.aes = FALSE,
  #   hjust = -0.2,
  #   size = 3,
  #   color = "black"
  # ) +
  facet_wrap(~ AttributeName, scales = "free_y") +
  scale_color_manual(values = group_colors) +
  scale_y_continuous(limits = c(0, 110)) +
  labs(
    title = "Willingness to Pay for Trail Improvements",
    x = "Management Level",
    y = "Average WTP per use ($)",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +
 theme(
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 16),   # facet titles: "Habitat Quality", "Trail Condition"
    legend.text  = element_text(size = 13),                # group names in legend
    legend.title = element_blank(),, # "Group" label
      panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(size = 12)

  )

print(p)
ggsave("WTP_incremental.png", p, width = 10, height = 6, dpi = 300)
```

# WTP Graph: Crowding

```{r}
# --- Step 1: Create Attribute level table 
attr_levels_crowding <- data.frame(
  Attribute = c("b_CrowdingMed", "b_CrowdingLow"),
  AttributeName = c("Crowding", "Crowding"),
  Level = c("Medium", "Low"),
  stringsAsFactors = FALSE
)

# Combine groups
wtp_all <- wtp_all_delta %>% mutate(Group = "All respondents")
wtp_res <- wtp_res_delta %>% mutate(Group = "Residents")
wtp_tour <- wtp_tour_delta %>% mutate(Group = "Tourists")

wtp_combined_crowding <- bind_rows(wtp_all, wtp_res, wtp_tour) %>%
  right_join(attr_levels_crowding, by = "Attribute")
```

```{r}
group_colors <- c("All respondents" = "grey", "Residents" = "#6a906c", "Tourists" = "#ae9864")

r <- ggplot(wtp_combined_crowding, aes(x = Level, y = wtp, color = Group, group = Group)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  # geom_errorbar(aes(ymin = lo95, ymax = hi95), width = 0.1, size = 0.5) +
  # Add value labels above points
  geom_text(aes(label = paste0("$", round(wtp))),
            vjust = -0.8,
            size = 3,
            show.legend = FALSE,
            fontface = "bold",
            color = "black") +     # use black for readability (or match group colors)
  facet_wrap(~ AttributeName, scales = "free_y") +
  scale_color_manual(values = group_colors) +
   scale_y_continuous(limits = c(0, 100)) + 
  labs(
    title = "Willingness to Pay for Trail Improvements",
    x = "Management Level",
    y = "Average WTP per use ($)",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +
 theme(
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 16),   # facet titles: "Crowding"
    legend.text  = element_text(size = 13),                # group names in legend
    legend.title = element_blank(),, # "Group" label
      panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(size = 12)

  )


print(r)
ggsave("WTP_incremental_Crowding.png", r, width = 10, height = 6, dpi = 300)
```

# Welfare Calculation

```{r}
# ══════════════════════════════════════════════════════
# SIMULATION-BASED WELFARE CALCULATION
# Mixed Logit — Parametric Normal Draws
# 1000 draws, attribute-by-attribute + bundle scenarios
# ══════════════════════════════════════════════════════

set.seed(123)  # for reproducibility
n_draws <- 1000

# ── Step 1: Extract means and SDs from estimated model ──
bhat <- model_mxl$estimate

# Means of random parameters
mu_HabitatMed    <- bhat["b_Habitat_QualityMed"]
mu_HabitatHigh   <- bhat["b_Habitat_QualityHigh"]
mu_TrailCondMed  <- bhat["b_Trail_ConditionMed"]
mu_TrailCondHigh <- bhat["b_Trail_ConditionHigh"]
mu_CrowdingMed   <- bhat["b_CrowdingMed"]
mu_CrowdingLow   <- bhat["b_CrowdingLow"]

# SDs of random parameters
sd_HabitatMed    <- abs(bhat["sd_Habitat_QualityMed"])
sd_HabitatHigh   <- abs(bhat["sd_Habitat_QualityHigh"])
sd_TrailCondMed  <- abs(bhat["sd_Trail_ConditionMed"])
sd_TrailCondHigh <- abs(bhat["sd_Trail_ConditionHigh"])
sd_CrowdingMed   <- abs(bhat["sd_CrowdingMed"])
sd_CrowdingLow   <- abs(bhat["sd_CrowdingLow"])

# Fixed parameters
b_cost     <- bhat["b_cost"]
asc_optout <- bhat["asc_optout"]

#Print output 
cat("═══════════════════════════════════════\n")
cat("Random parameter distributions:\n")
cat("═══════════════════════════════════════\n")
cat(sprintf("%-20s %8s %8s\n", "Parameter", "Mean", "SD"))
cat(sprintf("%-20s %8.4f %8.4f\n", "Habitat Med",    mu_HabitatMed,    sd_HabitatMed))
cat(sprintf("%-20s %8.4f %8.4f\n", "Habitat High",   mu_HabitatHigh,   sd_HabitatHigh))
cat(sprintf("%-20s %8.4f %8.4f\n", "TrailCond Med",  mu_TrailCondMed,  sd_TrailCondMed))
cat(sprintf("%-20s %8.4f %8.4f\n", "TrailCond High", mu_TrailCondHigh, sd_TrailCondHigh))
cat(sprintf("%-20s %8.4f %8.4f\n", "Crowding Med",   mu_CrowdingMed,   sd_CrowdingMed))
cat(sprintf("%-20s %8.4f %8.4f\n", "Crowding Low",   mu_CrowdingLow,   sd_CrowdingLow))
cat(sprintf("%-20s %8.4f %8s\n",   "Cost (fixed)",   b_cost,           "—"))
cat(sprintf("%-20s %8.4f %8s\n",   "ASC optout",     asc_optout,       "—"))

```

```{r}
# ── Step 2: Generate parametric draws ──
# Each draw r gives one complete set of preference parameters
# representing one "type" of individual from the population

draws <- data.frame(
  b_HabitatMed    = rnorm(n_draws, mu_HabitatMed,    sd_HabitatMed),
  b_HabitatHigh   = rnorm(n_draws, mu_HabitatHigh,   sd_HabitatHigh),
  b_TrailCondMed  = rnorm(n_draws, mu_TrailCondMed,  sd_TrailCondMed),
  b_TrailCondHigh = rnorm(n_draws, mu_TrailCondHigh, sd_TrailCondHigh),
  b_CrowdingMed   = rnorm(n_draws, mu_CrowdingMed,   sd_CrowdingMed),
  b_CrowdingLow   = rnorm(n_draws, mu_CrowdingLow,   sd_CrowdingLow)
)

cat("\nDraws generated:", n_draws, "\n")
cat("Verifying draw means match parameters:\n")
cat(sprintf("  b_HabitatMed mean:    %.4f (target: %.4f)\n", 
            mean(draws$b_HabitatMed), mu_HabitatMed))
cat(sprintf("  b_HabitatHigh mean:   %.4f (target: %.4f)\n", 
            mean(draws$b_HabitatHigh), mu_HabitatHigh))

```

```{r}
# ── Step 3: Define logsum function ──
# For each draw r, compute logsum per choice occasion
# then average across choice tasks per respondent
# then average across respondents and draws

compute_cv_sim <- function(_scenario, 
                           cost_alt1, cost_alt2,
                           b_cost_fixed, asc_optout_fixed,
                           draws_vec) {
  # draws_vec: vector of length n_draws — the simulated attribute utility
  # for this scenario under each draw
  
  cv_per_draw <- sapply(1:length(draws_vec), function(r) {
    
    # Baseline logsum (all attributes at reference = 0)
    V1_base <- b_cost_fixed * cost_alt1
    V2_base <- b_cost_fixed * cost_alt2
    V3_base <- rep(asc_optout_fixed, length(cost_alt1))
    ls_base  <- log(exp(V1_base) + exp(V2_base) + exp(V3_base))
    
    # Scenario logsum
    V1_scen <- draws_vec[r] + b_cost_fixed * cost_alt1
    V2_scen <- draws_vec[r] + b_cost_fixed * cost_alt2
    V3_scen <- rep(asc_optout_fixed, length(cost_alt1))
    ls_scen  <- log(exp(V1_scen) + exp(V2_scen) + exp(V3_scen))
    
    # CV per choice occasion
    cv_occ <- (ls_scen - ls_base) / (-b_cost_fixed)
    
    # Average across choice occasions (panel)
    mean(cv_occ)
  })
  
  return(cv_per_draw)
}
```

```{r}
# ── Step 4: Define all scenarios ──
# Each scenario is defined by which attribute coefficients are active
# Attribute utility for draw r = sum of relevant beta draws

cost_alt1 <- database$Cost.alt1
cost_alt2 <- database$Cost.alt2

scenarios <- list(
  # ── Individual attribute scenarios — Baseline → Medium ──
  "Habitat Quality: Low → Medium"   = draws$b_HabitatMed,
  "Habitat Quality: Low → High"     = draws$b_HabitatHigh,
  "Trail Condition: Low → Medium"   = draws$b_TrailCondMed,
  "Trail Condition: Low → High"     = draws$b_TrailCondHigh,
  "Crowding: High → Medium"         = draws$b_CrowdingMed,
  "Crowding: High → Low"            = draws$b_CrowdingLow,
  
  # ── Individual attribute scenarios — Medium → High ──
  # These are the DIFFERENCE between high and medium draws
  # Correctly propagates uncertainty across both estimates
  "Habitat Quality: Medium → High"  = draws$b_HabitatHigh - draws$b_HabitatMed,
  "Trail Condition: Medium → High"  = draws$b_TrailCondHigh - draws$b_TrailCondMed,
  "Crowding: Medium → Low"          = draws$b_CrowdingLow - draws$b_CrowdingMed,
  
  # ── Bundle scenarios ──
  "Medium Bundle (all → Medium)"    = 
    draws$b_HabitatMed + draws$b_TrailCondMed + draws$b_CrowdingMed,
  
  "High Bundle (all → High/Best)"   = 
    draws$b_HabitatHigh + draws$b_TrailCondHigh + draws$b_CrowdingLow,
  
  # ── Bundle Medium → High ──
  "Medium → High Bundle"            = 
    (draws$b_HabitatHigh - draws$b_HabitatMed) + 
    (draws$b_TrailCondHigh - draws$b_TrailCondMed) + 
    (draws$b_CrowdingLow - draws$b_CrowdingMed)
)
```

```{r}
# ── Step 5: Compute CV for each scenario ──
cat("\nRunning simulations...\n")

results_list <- lapply(names(scenarios), function(scen_name) {
  
  cat("  Computing:", scen_name, "\n")
  
  cv_draws <- compute_cv_sim(
    _scenario  = NULL,       # not used directly
    cost_alt1        = cost_alt1,
    cost_alt2        = cost_alt2,
    b_cost_fixed     = b_cost,
    asc_optout_fixed = asc_optout,
    draws_vec        = scenarios[[scen_name]]
  )
  
  tibble(
    Scenario  = scen_name,
    CV_mean   = mean(cv_draws),
    CV_median = median(cv_draws),
    CV_se     = sd(cv_draws),
    CV_lo95   = quantile(cv_draws, 0.025),
    CV_hi95   = quantile(cv_draws, 0.975)
  )
})

welfare_results <- bind_rows(results_list)

```

```{r}
# ── Step 6: Print results table ──
cat("\n")
cat("═══════════════════════════════════════════════════════════════════════\n")
cat("Simulation-Based Welfare Estimates (CV per person per trip)\n")
cat("1000 parametric draws from estimated MXL parameter distributions\n")
cat("═══════════════════════════════════════════════════════════════════════\n")
cat(sprintf("%-45s %8s %8s %20s\n", 
            "Scenario", "CV Mean", "SE", "95% Sim CI"))
cat(sprintf("%-45s %8s %8s %20s\n", 
            "—", "($)", "($)", ""))
cat("───────────────────────────────────────────────────────────────────────\n")

for(i in 1:nrow(welfare_results)) {
  cat(sprintf("%-45s %8.2f %8.2f   [%6.2f, %6.2f]\n",
              welfare_results$Scenario[i],
              welfare_results$CV_mean[i],
              welfare_results$CV_se[i],
              welfare_results$CV_lo95[i],
              welfare_results$CV_hi95[i]))
  
  # Separators between sections
  if(i == 6) cat("── Medium → High improvements ─────────────────────────────────────────\n")
  if(i == 9) cat("── Bundle scenarios ────────────────────────────────────────────────────\n")
}


cat("═══════════════════════════════════════════════════════════════════════\n")
cat("Note: CV = compensating variation. Positive values = welfare gains.\n")
cat("SE and CI derived from simulation across 1000 parameter draws.\n")
```

```{r}

# ── Step 7: Save results ──
write.csv(welfare_results, "welfare_simulation_results.csv", row.names = FALSE)
cat("\nResults saved to welfare_simulation_results.csv\n")
```

```{r}
# ══════════════════════════════════════════════════════
# DELTA METHOD CV — ATTRIBUTE BY ATTRIBUTE
# ══════════════════════════════════════════════════════

cv_single_delta <- function(model, attr_par, cost_par = "b_cost", 
                             scenario_name, use_robust = TRUE) {
  bhat <- model$estimate
  Vhat <- if(use_robust) model$robvarcov else model$varcov
  bc   <- bhat[cost_par]
  bk   <- bhat[attr_par]
  cv   <- bk / (-bc)
  grad <- c(d_bk = 1/(-bc), d_bc = bk/(bc^2))
  V2   <- as.matrix(Vhat[c(attr_par, cost_par), c(attr_par, cost_par)])
  se_cv <- sqrt(as.numeric(t(grad) %*% V2 %*% grad))
  tibble(Scenario = scenario_name,
         CV       = round(cv, 2),
         SE       = round(se_cv, 2),
         CI_low   = round(cv - 1.96 * se_cv, 2),
         CI_high  = round(cv + 1.96 * se_cv, 2))
}

cv_diff_delta <- function(model, attr_high, attr_med,
                           cost_par = "b_cost",
                           scenario_name, use_robust = TRUE) {
  bhat   <- model$estimate
  Vhat   <- if(use_robust) model$robvarcov else model$varcov
  bc     <- bhat[cost_par]
  b_high <- bhat[attr_high]
  b_med  <- bhat[attr_med]
  b_diff <- b_high - b_med
  cv     <- b_diff / (-bc)
  grad   <- c(d_bhigh = 1/(-bc), d_bmed = -1/(-bc), d_bc = b_diff/(bc^2))
  V3     <- as.matrix(Vhat[c(attr_high, attr_med, cost_par),
                            c(attr_high, attr_med, cost_par)])
  se_cv  <- sqrt(as.numeric(t(grad) %*% V3 %*% grad))
  tibble(Scenario = scenario_name,
         CV       = round(cv, 2),
         SE       = round(se_cv, 2),
         CI_low   = round(cv - 1.96 * se_cv, 2),
         CI_high  = round(cv + 1.96 * se_cv, 2))
}

cv_bundle_diff_delta <- function(model,
                                  attr_high_pars,
                                  attr_med_pars,
                                  cost_par = "b_cost",
                                  scenario_name,
                                  use_robust = TRUE) {
  bhat   <- model$estimate
  Vhat   <- if(use_robust) model$robvarcov else model$varcov
  bc     <- bhat[cost_par]
  b_high <- sum(bhat[attr_high_pars])
  b_med  <- sum(bhat[attr_med_pars])
  b_diff <- b_high - b_med
  cv     <- b_diff / (-bc)
  grad   <- c(rep(1/(-bc),  length(attr_high_pars)),
              rep(-1/(-bc), length(attr_med_pars)),
              b_diff/(bc^2))
  all_pars <- c(attr_high_pars, attr_med_pars, cost_par)
  V_block  <- as.matrix(Vhat[all_pars, all_pars])
  se_cv    <- sqrt(as.numeric(t(grad) %*% V_block %*% grad))
  tibble(Scenario = scenario_name,
         CV       = round(cv, 2),
         SE       = round(se_cv, 2),
         CI_low   = round(cv - 1.96 * se_cv, 2),
         CI_high  = round(cv + 1.96 * se_cv, 2))
}

# ══════════════════════════════════════════════════════
# Compute all CVs
# ══════════════════════════════════════════════════════
cv_individual <- bind_rows(
  
  # ── Habitat Quality ──
  cv_single_delta(model_mxl,
                  "b_Habitat_QualityMed",
                  scenario_name = "Habitat Quality: Low -> Medium"),
  cv_single_delta(model_mxl,
                  "b_Habitat_QualityHigh",
                  scenario_name = "Habitat Quality: Low -> High"),
  cv_diff_delta(model_mxl,
                attr_high     = "b_Habitat_QualityHigh",
                attr_med      = "b_Habitat_QualityMed",
                scenario_name = "Habitat Quality: Medium -> High"),
  
  # ── Trail Condition ──
  cv_single_delta(model_mxl,
                  "b_Trail_ConditionMed",
                  scenario_name = "Trail Condition: Low -> Medium"),
  cv_single_delta(model_mxl,
                  "b_Trail_ConditionHigh",
                  scenario_name = "Trail Condition: Low -> High"),
  cv_diff_delta(model_mxl,
                attr_high     = "b_Trail_ConditionHigh",
                attr_med      = "b_Trail_ConditionMed",
                scenario_name = "Trail Condition: Medium -> High"),
  
  # ── Crowding ──
  cv_single_delta(model_mxl,
                  "b_CrowdingMed",
                  scenario_name = "Crowding: High -> Medium"),
  cv_single_delta(model_mxl,
                  "b_CrowdingLow",
                  scenario_name = "Crowding: High -> Low"),
  cv_diff_delta(model_mxl,
                attr_high     = "b_CrowdingLow",
                attr_med      = "b_CrowdingMed",
                scenario_name = "Crowding: Medium -> Low"),
  
  # ── Bundles ──
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityMed",
                                "b_Trail_ConditionMed",
                                "b_CrowdingMed"),
              cost_par      = "b_cost",
              scenario_name = "Medium Bundle (all -> Medium)"),
  
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityHigh",
                                "b_Trail_ConditionHigh",
                                "b_CrowdingLow"),
              cost_par      = "b_cost",
              scenario_name = "High Bundle (all -> High/Best)"),
  
  # ── Medium to High Bundle ──
  cv_bundle_diff_delta(
    model_mxl,
    attr_high_pars = c("b_Habitat_QualityHigh",
                       "b_Trail_ConditionHigh",
                       "b_CrowdingLow"),
    attr_med_pars  = c("b_Habitat_QualityMed",
                       "b_Trail_ConditionMed",
                       "b_CrowdingMed"),
    cost_par       = "b_cost",
    scenario_name  = "Medium -> High Bundle"
  )
)  # <-- THIS closing parenthesis was missing before

# ══════════════════════════════════════════════════════
# Confirm row count before printing
# ══════════════════════════════════════════════════════
cat("Rows in cv_individual:", nrow(cv_individual), "\n")
print(cv_individual$Scenario)

# ══════════════════════════════════════════════════════
# Print priority setting table
# ══════════════════════════════════════════════════════
cat("\n")
cat("=================================================================\n")
cat("Welfare Estimates - Attribute Priority Setting Table\n")
cat("Delta method, mean coefficients, MXL pooled model\n")
cat("=================================================================\n")
cat(sprintf("%-42s %8s %8s %22s\n",
            "Scenario", "CV ($)", "SE ($)", "95% CI"))
cat("-----------------------------------------------------------------\n")

groups <- list(
  "Habitat Quality"  = 1:3,
  "Trail Condition"  = 4:6,
  "Crowding"         = 7:9,
  "Bundle Scenarios" = 10:12
)

for(grp_name in names(groups)) {
  cat(paste0("  [", grp_name, "]\n"))
  idx <- groups[[grp_name]]
  for(i in idx) {
    cat(sprintf("  %-40s %8.2f %8.2f   [%7.2f, %7.2f]\n",
                cv_individual$Scenario[i],
                cv_individual$CV[i],
                cv_individual$SE[i],
                cv_individual$CI_low[i],
                cv_individual$CI_high[i]))
  }
  cat("-----------------------------------------------------------------\n")
}

cat("Note: CV = compensating variation per person per trip.\n")
cat("All CIs exclude zero unless marked ns.\n")

# write.csv(cv_individual, "welfare_priority_table.csv", row.names = FALSE)
# cat("Saved to welfare_priority_table.csv\n")

```

### Scenario simulation

```{r}
# ══════════════════════════════════════════════════════
# COMBINED TABLE — Mean CV + Both CI types
# ══════════════════════════════════════════════════════

# ── Step 1: Run simulation for all scenarios ──
set.seed(123)
n_draws <- 1000

# Regenerate draws
draws <- data.frame(
  b_HabitatMed    = rnorm(n_draws, mu_HabitatMed,    sd_HabitatMed),
  b_HabitatHigh   = rnorm(n_draws, mu_HabitatHigh,   sd_HabitatHigh),
  b_TrailCondMed  = rnorm(n_draws, mu_TrailCondMed,  sd_TrailCondMed),
  b_TrailCondHigh = rnorm(n_draws, mu_TrailCondHigh, sd_TrailCondHigh),
  b_CrowdingMed   = rnorm(n_draws, mu_CrowdingMed,   sd_CrowdingMed),
  b_CrowdingLow   = rnorm(n_draws, mu_CrowdingLow,   sd_CrowdingLow)
)

# ── Step 2: Simulation CV per draw per scenario ──
# For each draw r, CV = sum(b_attr_r) / (-b_cost)
# b_cost is fixed so it doesn't vary across draws

sim_cv <- data.frame(
  
  # Individual attributes
  HabitatMed     = draws$b_HabitatMed    / (-b_cost),
  HabitatHigh    = draws$b_HabitatHigh   / (-b_cost),
  HabitatMedHigh = (draws$b_HabitatHigh - draws$b_HabitatMed) / (-b_cost),
  
  TrailCondMed   = draws$b_TrailCondMed  / (-b_cost),
  TrailCondHigh  = draws$b_TrailCondHigh / (-b_cost),
  TrailMedHigh   = (draws$b_TrailCondHigh - draws$b_TrailCondMed) / (-b_cost),
  
  CrowdingMed    = draws$b_CrowdingMed   / (-b_cost),
  CrowdingLow    = draws$b_CrowdingLow   / (-b_cost),
  CrowdingMedLow = (draws$b_CrowdingLow - draws$b_CrowdingMed) / (-b_cost),
  
  # Bundles
  BundleMed      = (draws$b_HabitatMed + 
                    draws$b_TrailCondMed + 
                    draws$b_CrowdingMed)  / (-b_cost),
  
  BundleHigh     = (draws$b_HabitatHigh + 
                    draws$b_TrailCondHigh + 
                    draws$b_CrowdingLow)  / (-b_cost),
  
  BundleMedHigh  = (draws$b_HabitatHigh - draws$b_HabitatMed +
                    draws$b_TrailCondHigh - draws$b_TrailCondMed +
                    draws$b_CrowdingLow  - draws$b_CrowdingMed)  / (-b_cost)
)

# ── Step 3: Extract simulation CIs ──
sim_summary <- data.frame(
  Scenario = c(
    "Habitat Quality: Low -> Medium",
    "Habitat Quality: Low -> High",
    "Habitat Quality: Medium -> High",
    "Trail Condition: Low -> Medium",
    "Trail Condition: Low -> High",
    "Trail Condition: Medium -> High",
    "Crowding: High -> Medium",
    "Crowding: High -> Low",
    "Crowding: Medium -> Low",
    "Medium Bundle (all -> Medium)",
    "High Bundle (all -> High/Best)",
    "Medium -> High Bundle"
  ),
  Sim_mean   = round(colMeans(sim_cv), 2),
  Sim_CI_low = round(apply(sim_cv, 2, quantile, 0.025), 2),
  Sim_CI_high= round(apply(sim_cv, 2, quantile, 0.975), 2)
)

# ── Step 4: Merge with delta method results ──
combined_table <- merge(
  cv_individual[, c("Scenario", "CV", "CI_low", "CI_high")],
  sim_summary[, c("Scenario", "Sim_CI_low", "Sim_CI_high")],
  by = "Scenario",
  sort = FALSE
)

# Restore original row order
combined_table <- combined_table[match(cv_individual$Scenario, 
                                        combined_table$Scenario), ]

# ── Step 5: Print combined table ──
cat("\n")
cat("================================================================\n")
cat("Welfare Estimates — Mean CV with Estimation and Heterogeneity CIs\n")
cat("================================================================\n")
cat(sprintf("%-38s %7s %18s %20s\n",
            "Scenario", "Mean CV",
            "Delta 95% CI",
            "Simulation 95% CI"))
cat(sprintf("%-38s %7s %18s %20s\n",
            "", "($)",
            "(estimation uncertainty)",
            "(preference heterogeneity)"))
cat("----------------------------------------------------------------\n")

groups <- list(
  "Habitat Quality"  = 1:3,
  "Trail Condition"  = 4:6,
  "Crowding"         = 7:9,
  "Bundle Scenarios" = 10:12
)

for(grp_name in names(groups)) {
  cat(paste0("  [", grp_name, "]\n"))
  idx <- groups[[grp_name]]
  for(i in idx) {
    cat(sprintf("  %-36s %7.2f  [%6.2f, %7.2f]    [%7.2f, %7.2f]\n",
                combined_table$Scenario[i],
                combined_table$CV[i],
                combined_table$CI_low[i],
                combined_table$CI_high[i],
                combined_table$Sim_CI_low[i],
                combined_table$Sim_CI_high[i]))
  }
  cat("----------------------------------------------------------------\n")
}

cat("\nNote: Delta CI = 95% CI from delta method reflecting estimation\n")
cat("uncertainty around mean CV. Simulation CI = 95% interval from\n")
cat("1000 parametric draws reflecting preference heterogeneity.\n")
```

```{r}
# ══════════════════════════════════════════════════════
# PARTIAL IMPROVEMENT SCENARIOS
# Management focuses on ONE attribute at a time
# Everything else stays at baseline (reference level)
# ══════════════════════════════════════════════════════

# ── Step 1: Define partial scenario CV using delta method ──
# These use cv_delta_se and cv_single_delta already defined

partial_scenarios <- bind_rows(
  
  # ════════════════════════════════
  # HABITAT QUALITY ONLY SCENARIOS
  # Trail condition = Low (ref)
  # Crowding = High (ref)
  # ════════════════════════════════
  cv_single_delta(model_mxl,
                  "b_Habitat_QualityMed",
                  scenario_name = "Habitat Only: Low → Medium"),
  
  cv_single_delta(model_mxl,
                  "b_Habitat_QualityHigh",
                  scenario_name = "Habitat Only: Low → High"),
  
  cv_diff_delta(model_mxl,
                attr_high     = "b_Habitat_QualityHigh",
                attr_med      = "b_Habitat_QualityMed",
                scenario_name = "Habitat Only: Medium → High"),
  
  # ════════════════════════════════
  # TRAIL CONDITION ONLY SCENARIOS
  # Habitat = Low (ref)
  # Crowding = High (ref)
  # ════════════════════════════════
  cv_single_delta(model_mxl,
                  "b_Trail_ConditionMed",
                  scenario_name = "Trail Condition Only: Low → Medium"),
  
  cv_single_delta(model_mxl,
                  "b_Trail_ConditionHigh",
                  scenario_name = "Trail Condition Only: Low → High"),
  
  cv_diff_delta(model_mxl,
                attr_high     = "b_Trail_ConditionHigh",
                attr_med      = "b_Trail_ConditionMed",
                scenario_name = "Trail Condition Only: Medium → High"),
  
  # ════════════════════════════════
  # CROWDING ONLY SCENARIOS
  # Habitat = Low (ref)
  # Trail condition = Low (ref)
  # ════════════════════════════════
  cv_single_delta(model_mxl,
                  "b_CrowdingMed",
                  scenario_name = "Crowding Only: High → Medium"),
  
  cv_single_delta(model_mxl,
                  "b_CrowdingLow",
                  scenario_name = "Crowding Only: High → Low"),
  
  cv_diff_delta(model_mxl,
                attr_high     = "b_CrowdingLow",
                attr_med      = "b_CrowdingMed",
                scenario_name = "Crowding Only: Medium → Low"),
  
  # ════════════════════════════════
  # HABITAT + TRAIL CONDITION (no crowding improvement)
  # Crowding stays at High (ref)
  # ════════════════════════════════
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityMed",
                                "b_Trail_ConditionMed"),
              cost_par      = "b_cost",
              scenario_name = "Habitat + Trail: Both → Medium"),
  
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityHigh",
                                "b_Trail_ConditionHigh"),
              cost_par      = "b_cost",
              scenario_name = "Habitat + Trail: Both → High"),
  
  # ════════════════════════════════
  # HABITAT + CROWDING (no trail condition improvement)
  # Trail condition stays at Low (ref)
  # ════════════════════════════════
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityMed",
                                "b_CrowdingMed"),
              cost_par      = "b_cost",
              scenario_name = "Habitat + Crowding: Both → Medium"),
  
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Habitat_QualityHigh",
                                "b_CrowdingLow"),
              cost_par      = "b_cost",
              scenario_name = "Habitat + Crowding: Both → High"),
  
  # ════════════════════════════════
  # TRAIL CONDITION + CROWDING (no habitat improvement)
  # Habitat stays at Low (ref)
  # ════════════════════════════════
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Trail_ConditionMed",
                                "b_CrowdingMed"),
              cost_par      = "b_cost",
              scenario_name = "Trail + Crowding: Both → Medium"),
  
  cv_delta_se(model_mxl,
              attr_pars     = c("b_Trail_ConditionHigh",
                                "b_CrowdingLow"),
              cost_par      = "b_cost",
              scenario_name = "Trail + Crowding: Both → High")
)

# ── Step 2: Add simulation CIs for partial scenarios ──
set.seed(123)

sim_partial <- data.frame(
  # Single attribute
  Hab_Med_only     = draws$b_HabitatMed    / (-b_cost),
  Hab_High_only    = draws$b_HabitatHigh   / (-b_cost),
  Hab_MedHigh_only = (draws$b_HabitatHigh - draws$b_HabitatMed) / (-b_cost),
  
  Trail_Med_only   = draws$b_TrailCondMed  / (-b_cost),
  Trail_High_only  = draws$b_TrailCondHigh / (-b_cost),
  Trail_MedHigh_only = (draws$b_TrailCondHigh - draws$b_TrailCondMed) / (-b_cost),
  
  Crowd_Med_only   = draws$b_CrowdingMed   / (-b_cost),
  Crowd_Low_only   = draws$b_CrowdingLow   / (-b_cost),
  Crowd_MedLow_only = (draws$b_CrowdingLow - draws$b_CrowdingMed) / (-b_cost),
  
  # Two attribute combinations
  HabTrail_Med     = (draws$b_HabitatMed  + draws$b_TrailCondMed)  / (-b_cost),
  HabTrail_High    = (draws$b_HabitatHigh + draws$b_TrailCondHigh) / (-b_cost),
  
  HabCrowd_Med     = (draws$b_HabitatMed  + draws$b_CrowdingMed)   / (-b_cost),
  HabCrowd_High    = (draws$b_HabitatHigh + draws$b_CrowdingLow)   / (-b_cost),
  
  TrailCrowd_Med   = (draws$b_TrailCondMed  + draws$b_CrowdingMed) / (-b_cost),
  TrailCrowd_High  = (draws$b_TrailCondHigh + draws$b_CrowdingLow) / (-b_cost)
)

# ── Clean bundle naming for presentation ──
bundle_labels <- data.frame(
  Scenario = c(
    # Bundle 1 — Habitat Quality only
    "Habitat Only: Low → Medium",
    "Habitat Only: Low → High",
    "Habitat Only: Medium → High",
    # Bundle 2 — Trail Condition only
    "Trail Condition Only: Low → Medium",
    "Trail Condition Only: Low → High",
    "Trail Condition Only: Medium → High",
    # Bundle 3 — Crowding only
    "Crowding Only: High → Medium",
    "Crowding Only: High → Low",
    "Crowding Only: Medium → Low",
    # Bundle 4 — Habitat + Trail Condition
    "Habitat + Trail: Both → Medium",
    "Habitat + Trail: Both → High",
    # Bundle 5 — Habitat + Crowding
    "Habitat + Crowding: Both → Medium",
    "Habitat + Crowding: Both → High",
    # Bundle 6 — Trail Condition + Crowding
    "Trail + Crowding: Both → Medium",
    "Trail + Crowding: Both → High"
  ),
  Bundle = c(
    rep("Bundle 1: Habitat Quality", 3),
    rep("Bundle 2: Trail Condition", 3),
    rep("Bundle 3: Crowding",        3),
    rep("Bundle 4: Habitat + Trail", 2),
    rep("Bundle 5: Habitat + Crowding", 2),
    rep("Bundle 6: Trail + Crowding",   2)
  ),
  Level = c(
    "Low → Medium", "Low → High", "Medium → High",
    "Low → Medium", "Low → High", "Medium → High",
    "High → Medium", "High → Low", "Medium → Low",
    "Both → Medium", "Both → High",
    "Both → Medium", "Both → High",
    "Both → Medium", "Both → High"
  )
)

# ── Merge bundle labels into partial_combined ──
partial_combined_labeled <- merge(
  partial_combined,
  bundle_labels,
  by       = "Scenario",
  sort     = FALSE
)

# Restore order
partial_combined_labeled <- partial_combined_labeled[
  match(partial_combined$Scenario, 
        partial_combined_labeled$Scenario), ]

# ── Print clean bundle table ──
three_bundle_table <- partial_combined_labeled %>%
  filter(Bundle %in% c(
    "Bundle 1: Habitat Quality",
    "Bundle 2: Trail Condition",
    "Bundle 3: Crowding"
  )) %>%
  select(Bundle, Level, CV, CI_low, CI_high, 
         Sim_CI_low, Sim_CI_high)

cat("\n")
cat("══════════════════════════════════════════════════════════════════════\n")
cat("Single Attribute Bundles — All Improvement Levels\n")
cat("All other attributes held at baseline (lowest level)\n")
cat("══════════════════════════════════════════════════════════════════════\n")
cat(sprintf("%-30s %-20s %8s %18s %22s\n",
            "Bundle", "Improvement Level",
            "CV ($)",
            "Delta 95% CI",
            "Simulation 95% CI"))
cat("──────────────────────────────────────────────────────────────────────\n")

for(bundle in unique(three_bundle_table$Bundle)) {
  cat(paste0("  [", bundle, "]\n"))
  bd <- three_bundle_table[three_bundle_table$Bundle == bundle, ]
  for(i in 1:nrow(bd)) {
    cat(sprintf("  %-30s %-20s %8.2f  [%6.2f,%7.2f]   [%7.2f,%7.2f]\n",
                "",
                bd$Level[i],
                bd$CV[i],
                bd$CI_low[i],
                bd$CI_high[i],
                bd$Sim_CI_low[i],
                bd$Sim_CI_high[i]))
  }
  cat("──────────────────────────────────────────────────────────────────────\n")
}

cat("Note: CV = compensating variation per person per trip.\n")
cat("Delta CI = estimation uncertainty.\n")
cat("Simulation CI = preference heterogeneity across individuals.\n")

# # ── Export labeled version ──
# write.csv(partial_combined_labeled,
#           "welfare_bundles_labeled.csv",
#           row.names = FALSE)
# cat("Saved to welfare_bundles_labeled.csv\n")



```

## Welfare Graph

```{r}
# ══════════════════════════════════════════════════════
# STEP 1: PREPARE DATA FOR CHARTS
# ══════════════════════════════════════════════════════

# ── Add simulation CIs to cv_individual ──
# Make sure combined_table exists from previous step
# If not, re-merge:
plot_data <- combined_table

# ── Label cleanup for plotting ──
plot_data$Scenario_clean <- c(
  # Habitat
  "Habitat:\nLow → Med",
  "Habitat:\nLow → High",
  "Habitat:\nMed → High",
  # Trail Condition
  "Trail Cond:\nLow → Med",
  "Trail Cond:\nLow → High",
  "Trail Cond:\nMed → High",
  # Crowding
  "Crowding:\nHigh → Med",
  "Crowding:\nHigh → Low",
  "Crowding:\nMed → Low",
  # Bundles
  "Medium\nBundle",
  "High\nBundle",
  "Med → High\nBundle"
)

# ── Split into individual and bundle ──
plot_individual <- plot_data[1:9, ]
plot_bundle     <- plot_data[10:12, ]

# ── Add attribute grouping for color coding ──
plot_individual$Attribute <- c(
  rep("Habitat Quality", 3),
  rep("Trail Condition", 3),
  rep("Crowding", 3)
)

plot_bundle$Attribute <- rep("Bundle", 3)

```

```{r}
# ══════════════════════════════════════════════════════
# STEP 2: CHART 1 — INDIVIDUAL ATTRIBUTES
# ══════════════════════════════════════════════════════

# Fix factor order for x axis
plot_individual$Scenario_clean <- factor(
  plot_individual$Scenario_clean,
  levels = plot_individual$Scenario_clean
)

chart1 <- ggplot(plot_individual, 
                 aes(x = Scenario_clean, y = CV, fill = Attribute)) +
  
  # Bars
  geom_bar(stat = "identity", width = 0.6, alpha = 0.85) +
  
  # Delta method CI (estimation uncertainty) — thin black whiskers
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),
                width = 0.15, linewidth = 0.8, color = "black") +
  
  # Simulation CI (preference heterogeneity) — wider grey whiskers
  geom_errorbar(aes(ymin = Sim_CI_low, ymax = Sim_CI_high),
                width = 0.25, linewidth = 0.5, 
                color = "grey40", linetype = "dashed") +
  
  # Zero reference line
  geom_hline(yintercept = 0, linewidth = 0.6, color = "black") +
  
  # Value labels on bars
  geom_text(aes(label = paste0("$", CV),
                y = ifelse(CV >= 0, CV + 3, CV - 3)),
            size = 3.2, fontface = "bold") +
  
  # Color scheme
  scale_fill_manual(values = c(
    "Habitat Quality" = "#2E8B57",   # forest green
    "Trail Condition" = "#4682B4",   # steel blue
    "Crowding"        = "#CD853F"    # peru/brown
  )) +
  
  # Labels
  labs(
    title    = "Welfare Gains from Individual Trail Attribute Improvements",
    subtitle = "Compensating variation per person per trip\nBlack bars = estimation uncertainty (delta method 95% CI)\nDashed grey bars = preference heterogeneity (simulation 95% CI)",
    x        = NULL,
    y        = "Compensating Variation ($ per person per trip)",
    fill     = "Attribute"
  ) +
  
  # Theme
  theme_minimal(base_size = 12) +
  theme(
    plot.title      = element_text(face = "bold", size = 13),
    plot.subtitle   = element_text(size = 9, color = "grey40"),
    axis.text.x     = element_text(size = 9, lineheight = 1.3),
    axis.text.y     = element_text(size = 10),
    legend.position = "bottom",
    legend.title    = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    plot.background    = element_rect(fill = "white", color = NA)
  )

print(chart1)
ggsave("welfare_chart1_individual.png", chart1, 
       width = 12, height = 7, dpi = 300, bg = "white")
cat("Chart 1 saved\n")

```

```{r}
# ══════════════════════════════════════════════════════
# STEP 3: CHART 2 — BUNDLE SCENARIOS
# ══════════════════════════════════════════════════════

plot_bundle$Scenario_clean <- factor(
  plot_bundle$Scenario_clean,
  levels = plot_bundle$Scenario_clean
)

chart2 <- ggplot(plot_bundle,
                 aes(x = Scenario_clean, y = CV)) +
  
  # Bars
  geom_bar(stat = "identity", width = 0.4, 
           fill = "#6A5ACD", alpha = 0.85) +
  
  # Delta method CI
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),
                width = 0.08, linewidth = 0.8, color = "black") +
  
  # Simulation CI
  geom_errorbar(aes(ymin = Sim_CI_low, ymax = Sim_CI_high),
                width = 0.15, linewidth = 0.5,
                color = "grey40", linetype = "dashed") +
  
  # Zero reference line
  geom_hline(yintercept = 0, linewidth = 0.6, color = "black") +
  
  # Value labels
  geom_text(aes(label = paste0("$", CV),
                y = CV + 6),
            size = 4, fontface = "bold") +
  
  # Y axis — extend to show full simulation CI
  scale_y_continuous(
    limits = c(
      min(plot_bundle$Sim_CI_low) - 20,
      max(plot_bundle$Sim_CI_high) + 40
    )
  ) +
  
  # Labels
  labs(
    title    = "Welfare Gains from Bundle Trail Improvement Scenarios",
    subtitle = "Compensating variation per person per trip — all attributes improved simultaneously\nBlack bars = estimation uncertainty (delta method 95% CI)\nDashed grey bars = preference heterogeneity (simulation 95% CI)",
    x        = NULL,
    y        = "Compensating Variation ($ per person per trip)"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 9, color = "grey40"),
    axis.text.x        = element_text(size = 11, lineheight = 1.3),
    axis.text.y        = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    plot.background    = element_rect(fill = "white", color = NA)
  )

print(chart2)
ggsave("welfare_chart2_bundles.png", chart2,
       width = 8, height = 7, dpi = 300, bg = "white")
cat("Chart 2 saved\n")
```

```{r}
# ══════════════════════════════════════════════════════
# STEP 4: ACCESS VALUE CALCULATION
# Value of having trail access vs opt-out only
# ══════════════════════════════════════════════════════

# ── Formula ──
# Access value = [logsum(with trails) - logsum(opt-out only)] / (-b_cost)
# logsum(opt-out only) = asc_optout (scalar, no cost term)
# logsum(with trails)  = log[exp(V1) + exp(V2) + exp(V3)]

compute_access_value <- function(, cost_alt1, cost_alt2,
                                  b_cost, asc_optout,
                                  scenario_name) {
  
  # Logsum with trail access
  V1 <-  + b_cost * cost_alt1
  V2 <-  + b_cost * cost_alt2
  V3 <- rep(asc_optout, length(cost_alt1))
  ls_access <- log(exp(V1) + exp(V2) + exp(V3))
  
  # Logsum without trail access (opt-out only)
  ls_no_access <- asc_optout  # scalar
  
  # Access value per choice occasion
  av_occ <- (ls_access - ls_no_access) / (-b_cost)
  
  # Average across choice occasions then respondents
  database$av <- av_occ
  av_respondent <- database %>%
    group_by(RID) %>%
    summarise(av = mean(av), .groups = "drop")
  
  tibble(
    Scenario     = scenario_name,
    Access_Value = round(mean(av_respondent$av), 2),
    Min          = round(min(av_respondent$av), 2),
    Max          = round(max(av_respondent$av), 2)
  )
}

# ── Compute access value for each scenario ──
access_values <- bind_rows(
  
  # Baseline — current degraded conditions
  compute_access_value(
           = 0,   # all attributes at reference level
    cost_alt1    = database$Cost.alt1,
    cost_alt2    = database$Cost.alt2,
    b_cost       = b_cost,
    asc_optout   = asc_optout,
    scenario_name = "Baseline (current conditions)"
  ),
  
  # Medium improvement
  compute_access_value(
           = as.numeric(bhat["b_Habitat_QualityMed"] +
                               bhat["b_Trail_ConditionMed"] +
                               bhat["b_CrowdingMed"]),
    cost_alt1    = database$Cost.alt1,
    cost_alt2    = database$Cost.alt2,
    b_cost       = b_cost,
    asc_optout   = asc_optout,
    scenario_name = "Medium improvement"
  ),
  
  # High improvement
  compute_access_value(
           = as.numeric(bhat["b_Habitat_QualityHigh"] +
                               bhat["b_Trail_ConditionHigh"] +
                               bhat["b_CrowdingLow"]),
    cost_alt1    = database$Cost.alt1,
    cost_alt2    = database$Cost.alt2,
    b_cost       = b_cost,
    asc_optout   = asc_optout,
    scenario_name = "High improvement"
  )
)

cat("\n")
cat("═══════════════════════════════════════════════════════\n")
cat("Access Value — Value of Trail Access vs Opt-Out\n")
cat("Per person per trip, mean across respondents\n")
cat("═══════════════════════════════════════════════════════\n")
cat(sprintf("%-30s %12s %10s %10s\n",
            "Scenario", "Access Value", "Min", "Max"))
cat("───────────────────────────────────────────────────────\n")
for(i in 1:nrow(access_values)) {
  cat(sprintf("%-30s %12.2f %10.2f %10.2f\n",
              access_values$Scenario[i],
              access_values$Access_Value[i],
              access_values$Min[i],
              access_values$Max[i]))
}
cat("═══════════════════════════════════════════════════════\n")
cat("Note: Access value = welfare gain from having trail\n")
cat("alternatives available vs opt-out only.\n")

```

## Total welfare measure

```{r}

# ══════════════════════════════════════════════════════
# TOTAL WELFARE CALCULATION
# Pooled model CV × hiking population × Na Ala Hele share
# ══════════════════════════════════════════════════════

# ══════════════════════════════════════════════════════
# STEP 1: POPULATION DATA
# ══════════════════════════════════════════════════════

# ── Island population and visitor data ──
# Replace with your exact numbers
island_data <- data.frame(
  Island = c("Oahu", "Maui", "Hawaii (Big Island)", 
             "Kauai"),
  #Based on 2024 census 
  Resident_pop = c(
    998747,   # Oahu 
    163769,    # Maui
    209790	,  # Big Island
    73840     # Kauai
  ),
  
  Annual_visitors = c(
    5794854,   # Oahu 
    2427626,   # Maui
    1735380,   # Big Island
    1393101   # Kauai
  )
)

# ── Total population (residents + visitors) ──
island_data$Total_pop <- island_data$Resident_pop + island_data$Annual_visitors

cat("═══════════════════════════════════════════════════════\n")
cat("Island Population Summary\n")
cat("═══════════════════════════════════════════════════════\n")
cat(sprintf("%-22s %12s %15s %12s\n",
            "Island", "Residents", "Visitors", "Total"))
cat("───────────────────────────────────────────────────────\n")
for(i in 1:nrow(island_data)) {
  cat(sprintf("%-22s %12s %15s %12s\n",
              island_data$Island[i],
              format(island_data$Resident_pop[i],   big.mark=","),
              format(island_data$Annual_visitors[i], big.mark=","),
              format(island_data$Total_pop[i],       big.mark=",")))
}
cat("───────────────────────────────────────────────────────\n")
cat(sprintf("%-22s %12s %15s %12s\n",
            "TOTAL HAWAII",
            format(sum(island_data$Resident_pop),   big.mark=","),
            format(sum(island_data$Annual_visitors), big.mark=","),
            format(sum(island_data$Total_pop),       big.mark=",")))
cat("═══════════════════════════════════════════════════════\n")

```

```{r}
# ══════════════════════════════════════════════════════
# STEP 2: PARAMETERS
# ══════════════════════════════════════════════════════

# ── Hiking participation rate ──
hiking_rate <- 0.40   # 40% of population hikes/backpacks

# ── Na Ala Hele share assumptions ──
# Range of assumptions for sensitivity analysis
nah_shares <- c(0.01, 0.05, 0.10)   # 1%, 5%, 10%
nah_labels <- c("Conservative (1%)", 
                "Moderate (5%)", 
                "Optimistic (10%)")

# ── CV values from your results ──
# Individual attributes
cv_values <- list(
  # Individual attribute improvements
  "Habitat Quality: Low -> Medium"   = combined_table$CV[
    combined_table$Scenario == "Habitat Quality: Low -> Medium"],
  "Habitat Quality: Low -> High"     = combined_table$CV[
    combined_table$Scenario == "Habitat Quality: Low -> High"],
  "Habitat Quality: Medium -> High"  = combined_table$CV[
    combined_table$Scenario == "Habitat Quality: Medium -> High"],
  "Trail Condition: Low -> Medium"   = combined_table$CV[
    combined_table$Scenario == "Trail Condition: Low -> Medium"],
  "Trail Condition: Low -> High"     = combined_table$CV[
    combined_table$Scenario == "Trail Condition: Low -> High"],
  "Trail Condition: Medium -> High"  = combined_table$CV[
    combined_table$Scenario == "Trail Condition: Medium -> High"],
  "Crowding: High -> Medium"         = combined_table$CV[
    combined_table$Scenario == "Crowding: High -> Medium"],
  "Crowding: High -> Low"            = combined_table$CV[
    combined_table$Scenario == "Crowding: High -> Low"],
  "Crowding: Medium -> Low"          = combined_table$CV[
    combined_table$Scenario == "Crowding: Medium -> Low"],
  # Bundle scenarios
  "Medium Bundle (all -> Medium)"    = combined_table$CV[
    combined_table$Scenario == "Medium Bundle (all -> Medium)"],
  "High Bundle (all -> High/Best)"   = combined_table$CV[
    combined_table$Scenario == "High Bundle (all -> High/Best)"],
  "Medium -> High Bundle"            = combined_table$CV[
    combined_table$Scenario == "Medium -> High Bundle"]
)

cat("\nCV values loaded:\n")
for(nm in names(cv_values)) {
  cat(sprintf("  %-40s $%.2f\n", nm, cv_values[[nm]]))
}
```

```{r}
# ══════════════════════════════════════════════════════
# STEP 3: TOTAL WELFARE CALCULATION
# Formula: CV × Total_pop × hiking_rate × nah_share
# ══════════════════════════════════════════════════════

# ── Function to compute total welfare ──
compute_welfare <- function(cv, total_pop, hiking_rate, nah_share) {
  # Number of trail users
  trail_users <- total_pop * hiking_rate * nah_share
  # Total welfare
  total_welfare <- cv * trail_users
  return(list(
    trail_users   = round(trail_users),
    total_welfare = round(total_welfare)
  ))
}

# ── Total Hawaii welfare across Na Ala Hele share scenarios ──
total_hawaii_pop <- sum(island_data$Total_pop)

cat("\n")
cat("═══════════════════════════════════════════════════════════════════════\n")
cat("Total Welfare — State of Hawaii\n")
cat("Based on 40% hiking participation rate\n")
cat("═══════════════════════════════════════════════════════════════════════\n")

# Build results table
welfare_results <- do.call(rbind, lapply(names(cv_values), function(scen) {
  do.call(rbind, lapply(1:length(nah_shares), function(j) {
    wf <- compute_welfare(cv_values[[scen]], 
                          total_hawaii_pop,
                          hiking_rate, 
                          nah_shares[j])
    data.frame(
      Scenario      = scen,
      NAH_share     = nah_labels[j],
      NAH_pct       = nah_shares[j] * 100,
      Trail_users   = wf$trail_users,
      CV_per_trip   = cv_values[[scen]],
      Total_welfare = wf$total_welfare,
      stringsAsFactors = FALSE
    )
  }))
}))

# ── Print by scenario group ──
scenario_groups <- list(
  "Habitat Quality"  = grep("Habitat",  names(cv_values), value=TRUE),
  "Trail Condition"  = grep("Trail",    names(cv_values), value=TRUE),
  "Crowding"         = grep("Crowding", names(cv_values), value=TRUE),
  "Bundle Scenarios" = grep("Bundle",   names(cv_values), value=TRUE)
)

for(grp in names(scenario_groups)) {
  cat(sprintf("\n  [%s]\n", grp))
  cat(sprintf("  %-38s %-22s %12s %18s\n",
              "Scenario", "NAH Share Assumption",
              "Trail Users", "Total Welfare ($)"))
  cat("  ", paste(rep("-", 90), collapse=""), "\n")
  
  for(scen in scenario_groups[[grp]]) {
    scen_data <- welfare_results[welfare_results$Scenario == scen, ]
    for(j in 1:nrow(scen_data)) {
      cat(sprintf("  %-38s %-22s %12s %18s\n",
                  ifelse(j==1, scen, ""),
                  scen_data$NAH_share[j],
                  format(scen_data$Trail_users[j],   big.mark=","),
                  paste0("$", format(round(scen_data$Total_welfare[j]/1e6, 2), 
                                     big.mark=","), "M")))
    }
    cat("\n")
  }
}
```

```{r}
# ══════════════════════════════════════════════════════
# STEP 4: ISLAND-LEVEL WELFARE BREAKDOWN
# Focus on bundle scenarios for island breakdown
# ══════════════════════════════════════════════════════

cat("═══════════════════════════════════════════════════════════════════════\n")
cat("Island-Level Welfare Breakdown — Bundle Scenarios\n")
cat("Moderate assumption: 10% Na Ala Hele share\n")
cat("═══════════════════════════════════════════════════════════════════════\n")

nah_share_main <- 0.10  # use moderate assumption for island breakdown

bundle_scenarios <- c(
  "Medium Bundle (all -> Medium)",
  "High Bundle (all -> High/Best)",
  "Medium -> High Bundle"
)

for(scen in bundle_scenarios) {
  cat(sprintf("\n  Scenario: %s (CV = $%.2f/person/trip)\n", 
              scen, cv_values[[scen]]))
  cat(sprintf("  %-22s %12s %12s %18s\n",
              "Island", "Total Pop", "Trail Users", "Total Welfare"))
  cat("  ", paste(rep("-", 66), collapse=""), "\n")
  
  island_welfare <- island_data %>%
    mutate(
      Trail_users   = round(Total_pop * hiking_rate * nah_share_main),
      Total_welfare = round(cv_values[[scen]] * Trail_users)
    )
  
  for(i in 1:nrow(island_welfare)) {
    cat(sprintf("  %-22s %12s %12s %18s\n",
                island_welfare$Island[i],
                format(island_welfare$Total_pop[i],   big.mark=","),
                format(island_welfare$Trail_users[i], big.mark=","),
                paste0("$", format(round(island_welfare$Total_welfare[i]/1e6, 2),
                                   big.mark=","), "M")))
  }
  cat("  ", paste(rep("-", 66), collapse=""), "\n")
  cat(sprintf("  %-22s %12s %12s %18s\n",
              "TOTAL HAWAII",
              format(sum(island_welfare$Total_pop),   big.mark=","),
              format(sum(island_welfare$Trail_users), big.mark=","),
              paste0("$", format(round(sum(island_welfare$Total_welfare)/1e6, 2),
                                 big.mark=","), "M")))
}
```

```{r}
# ══════════════════════════════════════════════════════
# STEP 5: SENSITIVITY ANALYSIS CHART
# Show how total welfare varies across NAH share assumptions
# Focus on bundle scenarios
# ══════════════════════════════════════════════════════


bundle_welfare_clean <- bundle_welfare %>%
  filter(Scenario %in% c(
    "Medium Bundle (all -> Medium)",
    "High Bundle (all -> High/Best)"
  )) %>%
  mutate(
    Scenario_clean = case_when(
      grepl("Medium Bundle", Scenario) ~ "Medium\nBundle",
      grepl("High Bundle",   Scenario) ~ "High\nBundle"
    ),
    Scenario_clean = factor(Scenario_clean, 
                            levels = c("Medium\nBundle", "High\nBundle")),
    NAH_share = factor(NAH_share, levels = nah_labels)
  )

# Verify data looks right before plotting
cat("\nCleaned data for chart:\n")
print(bundle_welfare_clean[, c("Scenario_clean", "NAH_share", "Total_welfare_M")])

sensitivity_chart_clean <- ggplot(bundle_welfare_clean,
                                   aes(x    = Scenario_clean,
                                       y    = Total_welfare_M,
                                       fill = NAH_share)) +
  
  geom_bar(stat     = "identity",
           position = position_dodge(width = 0.75),
           width    = 0.65,
           alpha    = 0.85) +
  
  geom_text(aes(label = paste0("$", round(Total_welfare_M, 0), "M"),
                y     = Total_welfare_M + 1.5),
            position  = position_dodge(width = 0.75),
            size      = 3.8,
            fontface  = "bold") +
  
  scale_fill_manual(values = c(
    "Conservative (1%)"  = "#CD853F",
    "Moderate (5%)"     = "#4682B4",
    "Optimistic (10%)"   = "#2E8B57"
  )) +
  
  scale_y_continuous(
    labels   = function(x) paste0("$", x, "M"),
    expand   = expansion(mult = c(0, 0.15))
  ) +
  
  labs(
    title    = "Total Welfare by Policy Scenario and Na Ala Hele Trail Share Assumption",
    subtitle = paste0(
      "Based on 40% hiking participation rate across total Hawaii population\n",
      "Na Ala Hele share assumptions: Conservative (1%), Moderate (5%), Optimistic (10%)"
    ),
    x        = "Policy Scenario",
    y        = "Total Welfare ($ millions)",
    fill     = "Na Ala Hele\nTrail Share"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 9, color = "grey40"),
    axis.text.x        = element_text(size = 12, lineheight = 1.3),
    axis.text.y        = element_text(size = 10),
    legend.position    = "right",
    legend.title       = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    plot.background    = element_rect(fill = "white", color = NA)
  )

print(sensitivity_chart_clean)
ggsave("total_welfare_sensitivity_clean.png", sensitivity_chart_clean,
       width = 10, height = 7, dpi = 300, bg = "white")
cat("Clean chart saved\n")
```

```{r}
# ══════════════════════════════════════════════════════
# TOTAL WELFARE BY BUNDLE — STATEWIDE HAWAII
# Single attribute bundles + combination bundles
# ══════════════════════════════════════════════════════

# ── Step 1: Verify CV values by position ──
cat("partial_combined_labeled CV values (rows 1-9):\n")
print(partial_combined_labeled[1:9, c("Scenario", "CV")])

cat("\ncombined_table CV values (rows 10-12):\n")
print(combined_table[10:12, c("Scenario", "CV")])

# ── Step 2: Build bundle_cv using positional indexing ──
bundle_cv <- data.frame(
  Bundle_group = c(
    rep("Bundle 1: Habitat Quality",   3),
    rep("Bundle 2: Trail Condition",   3),
    rep("Bundle 3: Crowding",          3),
    rep("Full Bundle: All Attributes", 3)
  ),
  Level = c(
    "Low → Medium",  "Low → High",  "Medium → High",
    "Low → Medium",  "Low → High",  "Medium → High",
    "High → Medium", "High → Low",  "Medium → Low",
    "All → Medium",  "All → High",  "Medium → High"
  ),
  CV = c(
    # Bundle 1 — Habitat only (rows 1,2,3)
    partial_combined_labeled$CV[1],
    partial_combined_labeled$CV[2],
    partial_combined_labeled$CV[3],
    # Bundle 2 — Trail condition only (rows 4,5,6)
    partial_combined_labeled$CV[4],
    partial_combined_labeled$CV[5],
    partial_combined_labeled$CV[6],
    # Bundle 3 — Crowding only (rows 7,8,9)
    partial_combined_labeled$CV[7],
    partial_combined_labeled$CV[8],
    partial_combined_labeled$CV[9],
    # Full bundles from combined_table (rows 10,11,12)
    combined_table$CV[10],
    combined_table$CV[11],
    combined_table$CV[12]
  ),
  stringsAsFactors = FALSE
)

cat("\nBundle CV values — all should be different:\n")
print(bundle_cv)

# ── Step 3: Compute total welfare ──
total_hawaii_pop <- sum(island_data$Total_pop)
hiking_rate      <- 0.40
nah_shares       <- c(0.01, 0.05, 0.10)
nah_labels       <- c("Conservative (1%)",
                       "Moderate (5%)",
                       "Optimistic (10%)")

welfare_bundle <- do.call(rbind, lapply(1:nrow(bundle_cv), function(i) {
  do.call(rbind, lapply(1:length(nah_shares), function(j) {
    trail_users   <- total_hawaii_pop * hiking_rate * nah_shares[j]
    total_welfare <- bundle_cv$CV[i] * trail_users
    data.frame(
      Bundle_group    = bundle_cv$Bundle_group[i],
      Level           = bundle_cv$Level[i],
      CV              = bundle_cv$CV[i],
      NAH_label       = nah_labels[j],
      NAH_pct         = nah_shares[j] * 100,
      Trail_users     = round(trail_users),
      Total_welfare   = round(total_welfare),
      Total_welfare_M = round(total_welfare / 1e6, 2),
      stringsAsFactors = FALSE
    )
  }))
}))

```

```{r}

# ── Step 4: Print welfare table ──
cat("\n")
cat("══════════════════════════════════════════════════════════════════════════\n")
cat("Total Welfare by Bundle — State of Hawaii\n")
cat("40% hiking participation rate\n")
cat("══════════════════════════════════════════════════════════════════════════\n")
cat(sprintf("%-28s %-16s %-22s %12s %15s\n",
            "Bundle", "Level", "NAH Share", "Trail Users", "Total Welfare"))
cat("──────────────────────────────────────────────────────────────────────────\n")

for(grp in unique(welfare_bundle$Bundle_group)) {
  cat(paste0("\n  [", grp, "]\n"))
  grp_data <- welfare_bundle[welfare_bundle$Bundle_group == grp, ]
  
  for(lvl in unique(grp_data$Level)) {
    lvl_data <- grp_data[grp_data$Level == lvl, ]
    cat(sprintf("  Improvement: %s\n", lvl))
    
    for(j in 1:nrow(lvl_data)) {
      cat(sprintf("    %-22s %12s %15s\n",
                  lvl_data$NAH_label[j],
                  format(lvl_data$Trail_users[j], big.mark=","),
                  paste0("$", format(lvl_data$Total_welfare_M[j],
                                     big.mark=","), "M")))
    }
    cat("\n")
  }
  cat("──────────────────────────────────────────────────────────────────────────\n")
}

```

```{r}
# ── Step 5 - Updated chart with cleaner labels ──
chart_data <- chart_data %>%
  mutate(
    Bundle_clean = case_when(
      Bundle_group == "Bundle 1: Habitat Quality"   ~ "Bundle 1\nHabitat Quality",
      Bundle_group == "Bundle 2: Trail Condition"   ~ "Bundle 2\nTrail Condition",
      Bundle_group == "Bundle 3: Crowding"          ~ "Bundle 3\nCrowding",
      Bundle_group == "Full Bundle: All Attributes" ~ "Full Bundle\nAll Attributes"
    ),
    Bundle_clean = factor(Bundle_clean, levels = c(
      "Bundle 1\nHabitat Quality",
      "Bundle 2\nTrail Condition",
      "Bundle 3\nCrowding",
      "Full Bundle\nAll Attributes"
    ))
  )

bundle_welfare_chart_clean <- ggplot(chart_data,
                                      aes(x    = Bundle_clean,
                                          y    = Total_welfare_M,
                                          fill = NAH_label)) +
  
  geom_bar(stat     = "identity",
           position = position_dodge(width = 0.75),
           width    = 0.65,
           alpha    = 0.85) +
  
  geom_text(aes(label = paste0("$", Total_welfare_M, "M"),
                y     = Total_welfare_M + 0.5),
            position  = position_dodge(width = 0.75),
            size      = 3.2,
            fontface  = "bold") +
  
  scale_fill_manual(values = c(
    "Conservative (1%)" = "#CD853F",
    "Moderate (5%)"     = "#4682B4",
    "Optimistic (10%)"  = "#2E8B57"
  )) +
  
  scale_y_continuous(
    labels = function(x) paste0("$", x, "M"),
    expand = expansion(mult = c(0, 0.15))
  ) +
  
  labs(
    title    = "Total Welfare Gains by Management Bundle (Low to High Improvement)",
    subtitle = paste0(
      "~ 10 million visitors",
      "40% hiking participation rate\n",
      "Na Ala Hele share assumptions: 1% (conservative), ",
      "5% (moderate), 10% (optimistic)"
    ),
    x    = "Management Bundle",
    y    = "Total Welfare ($ millions)",
    fill = "Na Ala Hele\nTrail Share"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 12),
    plot.subtitle      = element_text(size = 9, color = "grey40"),
    axis.text.x        = element_text(size = 11, lineheight = 1.3),
    axis.text.y        = element_text(size = 10),
    legend.position    = "right",
    legend.title       = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    plot.background    = element_rect(fill = "white", color = NA)
  )

print(bundle_welfare_chart_clean)
ggsave("total_welfare_by_bundle_clean.png", bundle_welfare_chart_clean,
       width = 12, height = 7, dpi = 300, bg = "white")
cat("Clean chart saved\n")
```

```{r}
# ══════════════════════════════════════════════════════
# TOTAL WELFARE BY IMPROVEMENT LEVEL
# Fixed NAH share = 10%
# Focus: welfare gain as improvement level increases
# ══════════════════════════════════════════════════════

# ── Fixed parameters — 10 million annual visitors ──
hiking_rate       <- 0.40
total_visitors    <- 10000000  # approximate annual Hawaii visitor arrivals
trail_users_fixed <- round(total_visitors * hiking_rate)

cat("═══════════════════════════════════════════\n")
cat("Fixed assumptions:\n")
cat("Annual Hawaii visitors: ~10 million\n")
cat("Hiking rate:             40%\n")
cat("Estimated trail users:  ", format(trail_users_fixed, big.mark=","), "\n")
cat("═══════════════════════════════════════════\n")

# ── Recompute Total_welfare_M ──
welfare_levels <- welfare_levels %>%
  mutate(Total_welfare_M = round(CV * trail_users_fixed / 1e6, 2))

# ── Refilter for chart ──
welfare_levels_chart <- welfare_levels %>%
  filter(Level_clean != "Baseline (No improvement)") %>%
  mutate(
    Bundle_clean = case_when(
      Bundle_group == "Bundle 1: Habitat Quality"   ~ "Habitat\nQuality",
      Bundle_group == "Bundle 2: Trail Condition"   ~ "Trail\nCondition",
      Bundle_group == "Bundle 3: Crowding"          ~ "Crowding",
      Bundle_group == "Full Bundle: All Attributes" ~ "All\nAttributes"
    ),
    Bundle_clean = factor(Bundle_clean, levels = c(
      "Habitat\nQuality",
      "Trail\nCondition",
      "Crowding",
      "All\nAttributes"
    ))
  )

# ── Plot ──
bundle_level_chart_visitors <- ggplot(welfare_levels_chart,
                                       aes(x    = Bundle_clean,
                                           y    = Total_welfare_M,
                                           fill = Level_clean)) +
  
  geom_bar(stat     = "identity",
           position = position_dodge(width = 0.75),
           width    = 0.65,
           alpha    = 0.85) +
  
  geom_text(aes(label = paste0("$", Total_welfare_M, "M"),
                y     = Total_welfare_M + max(Total_welfare_M) * 0.03),
            position  = position_dodge(width = 0.75),
            size      = 4.5,
            fontface  = "bold") +
  
  scale_fill_manual(values = c(
    "Medium Improvement" = "#4682B4",
    "High Improvement"   = "#2E8B57"
  )) +
  
  scale_y_continuous(
    labels = function(x) paste0("$", x, "M"),
    expand = expansion(mult = c(0, 0.15))
  ) +
  
labs(
  title    = "Estimated Public Benefits of Trail Improvements by Management Focus",
  subtitle = paste0(
    "~10 million annual visitors | ",
    "40% hiking participation rate\n"
  ),
  x    = "Management Focus",
  y    = "Estimated Public Benefits ($ millions)",
  fill = "Improvement Level"
) +
  
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14),
    plot.subtitle      = element_text(size = 11, color = "black"),
    axis.text.x        = element_text(size = 12, color = "black",
                                      lineheight = 1.3),
    axis.text.y        = element_text(size = 10),
    legend.position    = "right",
    legend.title       = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    plot.background    = element_rect(fill = "white", color = NA)
  )

print(bundle_level_chart_visitors)
ggsave("total_welfare_by_level_clean.png", bundle_level_chart_visitors,
       width = 12, height = 7, dpi = 300, bg = "white")
cat("Clean chart saved\n")
```

```{r}
# ── Verify numbers ──
cat("\nTotal welfare check — no NAH share:\n")
print(welfare_levels_chart[, c("Bundle_clean", "Level_clean",
                                "CV", "Total_welfare_M")])
```
